---
title: "NCRN Forest Vegetation QC"
output: html_document
knit: (function(inputFile, encoding) { 
          rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file='NCRN_Forest_Veg_QC.html') })

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(NPSForVeg)
library(tidyverse)
library(DT)
library(lubridate)

options(htmlwidgets.TOJSON_ARGS = list(na = 'string'))

NiceTable<-function(DF){
   

   datatable(DF, rownames = F, extensions = "Buttons", autoHideNavigation = T, options=list(
      columnDefs=list(list(className='dt-center', targets=0:ncol(DF)-1 )),
      pageLength=25,
      dom='Btip',
      buttons=c('copy','csv'))
   )}

errorText<-function(text) {cat(paste0("<span style='color:red;'>",text,"</span><br>"))}

#DataDir<-"C:/Data/NCRN_Veg_2020"

#DataDir<-"C:/Users/jschmit/OneDrive - DOI/Data/NCRN_Veg_2024"
DataDir<-"C:/Users/jschmit/OneDrive - DOI/Data/NCRN_Veg_2024/"

NCRN<-importNCRN(DataDir)

#QCYears<-c(2008, 2012,2016, 2021)
QCYears<-c(2020:2021)
QCPastYears<-c(2016, 2012, 2008)
QCAllYears<-unique(c(QCYears, QCPastYears))
QCLastSample<-2016


# Bad_Species<-c("Carya tomentosa", "Hicoria cordiformis", "Quercus prinus", "Robinia pseudo-acacia", "Rulac negundo", "Sassafras officinale",
#                "Polycodium stamineum", "Vaccinium atrococcum", "Vaccinium constablaei",
#                "Alliaria officinalis", "Eulalia viminea","Nepeta hederacea", "Polygonum cespitosum","Rosa cathayensis","Smilax hispida")



QCPlots<-getPlots(NCRN, years = QCYears, type="all" ) %>% mutate(Aspect= as.numeric(Aspect))

QCEvents<-getEvents(NCRN, years = QCYears)
QCAllEvents<-getEvents(NCRN, years = QCAllYears)

QCCWD<-getPlants(NCRN, "cwd", years=QCYears) #%>% filter(!Latin_Name %in% Bad_Species)

QCTrees<-getPlants(NCRN,"trees", years=QCYears, status = "all") #%>% filter(!Latin_Name %in% Bad_Species)
QCLastTrees<-getPlants(NCRN,"trees", years=QCLastSample, status = "all") 
QCAllTrees<-getPlants(NCRN,"trees", years=QCAllYears, status = "all") #%>% filter(!Latin_Name %in% Bad_Species)

QCSaplings<-getPlants(NCRN, "saplings",  years=QCYears, status="all") #%>% filter(!Latin_Name %in% Bad_Species)
QCLastSaplings<-getPlants(NCRN,"saplings", years=QCLastSample, status = "all") 
QCAllSaplings<-getPlants(NCRN, "saplings",  years=QCAllYears, status="all")# %>% filter(!Latin_Name %in% Bad_Species)

QCAllStems<-read.csv(paste0(DataDir,"/Stems.csv"), stringsAsFactors = F)#, !Latin_Name %in% Bad_Species)
QCStems<-QCAllStems %>% filter(Sample_Year %in% QCYears)
QCStemSummary<-QCAllStems |> summarize(Live_Stems=sum(Live==1), Dead_Stems=sum(Live==0), .by=c(Tag, Sample_Year))

QCShrubs<-getPlants(NCRN, "shrubs",  years=QCYears, status="all") #%>% filter(!Latin_Name %in% Bad_Species)
QCLastShrubs<-getPlants(NCRN,"shrubs", years=QCLastSample, status = "all") 
QCAllShrubs<-getPlants(NCRN, "shrubs",  years=QCAllYears, status="all") #%>% filter(!Latin_Name %in% Bad_Species)

QCConditions<-read.csv(paste0(DataDir,"/Tree_Sapling_Conditions.csv"), stringsAsFactors = F) %>% 
   filter(Sample_Year %in% QCYears)#, !Latin_Name %in% Bad_Species)

QCAllConditions<-read.csv(paste0(DataDir,"/Tree_Sapling_Conditions.csv"), stringsAsFactors = F) %>% 
   filter(Sample_Year %in% QCAllYears)#, !Latin_Name %in% Bad_Species)


QCFoliage<-read.csv(paste0(DataDir,"/Foliage_Conditions.csv"), stringsAsFactors = F) %>% filter(Sample_Year %in% QCYears)#, !Latin_Name %in% Bad_Species)

QCVines<-getPlants(NCRN,"vines",  years=QCYears )# %>% filter(!Latin_Name %in% Bad_Species)
QCAllVines<-getPlants(NCRN,"vines",  years=QCAllYears )# %>% filter(!Latin_Name %in% Bad_Species)

QCQuads<-read.csv(paste0(DataDir,"/Quadrat_Conditions.csv"), stringsAsFactors = F) %>% filter(Sample_Year %in% QCYears)
QCAllQuads<-read.csv(paste0(DataDir,"/Quadrat_Conditions.csv"), stringsAsFactors = F) %>% filter(Sample_Year %in% QCAllYears)

QCSeedlings<-rbind(getPlants(NCRN,"seedlings", years=QCYears),getPlants(NCRN,"shseedlings", years=QCYears) )# %>% filter(!Latin_Name %in% Bad_Species)

QCHerbs<-getPlants(NCRN, "herbs", years=QCYears) #%>% filter(!Latin_Name %in% Bad_Species)


QCTags<-read.csv(paste0(DataDir,"/Tag_History.csv"), stringsAsFactors = F) %>% filter(Location_Status!="Retired")
QCTags_Long<-QCTags %>% pivot_longer(cols=starts_with("X"), names_to="Raw_Cycle", values_to="Plant_Status") %>% 
  mutate(Cycle=gsub("X","", Raw_Cycle) %>% as.numeric)
QCTags_Latest<-QCTags_Long %>% filter(Plant_Status!="") %>% group_by(Tag) %>% 
  mutate(Missing_Events=sum(Plant_Status %in% c("Tree - Missing",  "Tree - Dead Missing",
                "Tree - Missing - Presumed Dead", "Tree - Missing - Uncertain", "Sapling - Missing",
                 "Sapling - Missing - Presumed Dead", "Sapling - Missing - Uncertain"))) %>% 
  filter(Cycle==max(Cycle)) %>% ungroup()

All_Plants<-rbind(getPlants(NCRN,"trees") %>% select(Tag,Latin_Name),
                  getPlants(NCRN,"saplings") %>% select(Tag,Latin_Name),
              getPlants(NCRN,"shrubs") %>% select(Tag,Latin_Name) ) %>% distinct

QCTags_Latest<-QCTags_Latest %>% left_join(All_Plants)
QCWoodies<-bind_rows( QCTrees %>% select(Unit_Code,Plot_Name, Tag, Latin_Name, TSN, Cycle, Sample_Year, Status),   # used for conditions, foliage, vines
                      QCSaplings %>% select(Unit_Code, Plot_Name, Tag, Latin_Name, TSN, Cycle, Sample_Year, Status),
                      QCShrubs %>% select(Unit_Code, Plot_Name, Tag, Latin_Name, TSN, Cycle, Sample_Year, Status))


QCAllWoodies<-bind_rows( QCAllTrees %>% select(Unit_Code,Plot_Name, Tag, Latin_Name, TSN, Cycle, Sample_Year, Status), 
                      QCAllSaplings %>% select(Unit_Code, Plot_Name, Tag, Latin_Name, TSN, Cycle, Sample_Year, Status),
                      QCAllShrubs %>% select(Unit_Code, Plot_Name, Tag, Latin_Name, TSN, Cycle, Sample_Year, Status))

Repeat_Woodies<-QCAllWoodies %>% group_by(Tag) %>% summarize(Records=n()) %>% filter(Records>1) %>% pull(Tag)



QCCommonNames<-read.csv(paste0(DataDir,"/CommonNames.csv"), stringsAsFactors = F)
# QCPlotFloor<-read.csv(paste0(DataDir,"/Plot_Floor.csv"), stringsAsFactors = F) %>% filter(Sample_Year %in% QCYears)
# QCTags<-read.csv(paste0(DataDir,"/Tag_History.csv"), stringsAsFactors = F)



Live_Status<-c("Alive Broken", "Alive Fallen", "Alive Leaning", "Alive Standing")
Dead_Status<-c("Dead", "Dead - Human Action", "Dead - Too Small", "Dead Fallen", "Dead Leaning", "Dead Missing", "Dead Standing")
Missing_Status<-c("Missing", "Missing - Presumed Dead", "Missing - Uncertain")
Other_Status<-c( "Downgraded to Non-Sampled")

Vigor_Options<-c("Healthy", "Light Decline", "Moderate Decline","Severe Decline", "Functionally Dead")


```



```{css, echo=FALSE}
h1, h2, h3 {
  text-align: center;
}

.nav>li>a {
   padding: 10px;
}
```

#  {.tabset .tabset-pills .tabset-fade}

## Introduction

**Run on:** `r format(Sys.Date(),"%B %d %Y") `.

**Years covered:** `r paste0(min(QCYears),"-", max(QCYears)) `.


### The following data is not currently QCed:

#### All
- Flags are not exported from the database and are not considered during QC.

- Sub-unit codes need to be revisited

- Need a mechanism to check if Latin names are reasonable

- Need a way to check about tags being retired

- Need a way to check that we don't export data for plants that have been removed from study

- Need to export Class and Habit for all relevant tables (Foliage in particular)

- Exotic Status is sometimes exported and sometimes not

- Browsing data is inconsistent between Seedlings and Herbs

#### Plots
- Retired date for retired plots not currently recorded and should be revisited.

#### Events
- Need to export table that matches years with panels so we can verify the correct plots were sampled.

- Need to consider if and how to handle Invasive, rare and plot maintenance checks before they were part of interface.

#### Saplings
- Around 1680 saplings and shrubs not currently exported due to not having habit filled in. Many are removed from study and would not be exported

- Equivalent diameter and Sum basal area is not exported for dead stems of saplings (this will typically = 0)

- Dead shrubs with no "habit" are exported as saplings

#### Stems
- Dead stems not exported

#### Shrubs
- Around 750 saplings and shrubs not currently exported due to not having habit filled in. 

- Need  a mechanism to check if Latin names are reasonable

- Need to export the foliage conditions, tree conditions and vines check-boxes. Need to verify they are checked for living shrubs, and  have conditions checked from 2015(?) on, but not checked in other cases.

#### Conditions
- Trees (and saplings) with no conditions are still listed in the Tree_Sapling_Conditions export - eliminate. This is not true of Shrubs

- In Tree_Conditions export there is no way to separate saplings and shrubs from trees (compare to stems export which has Habit and Class fields )

#### Quads
- Need to export table that matches years with panels so we can verify the correct quads were sampled.


#### Seedlings
- Seedling number / height/ species - need to determine if these are consistent enough between samples for QC or not

#### Understory Plants
- Need to export Herb browsable and browse data

- Current QC looks at large changes in herb %, additions of species and loss of species - are herb % consistent enough between samples  to use as QC? What about species lists? Need to check data.

#### Tags
- Need to check that all tags that should be monitored are, and that none that should not be monitored are monitored

## Plots

```{r Plot-QC, child="01_ForestVegPlotsQC.Rmd"}
```


## Events

```{r Event-QC, child="02_ForestVegEventsQC.Rmd"}
```

## Plot Floor

```{r Plot_Floor-QC, child="03_ForestVegPlotFloorQC.Rmd"}
```

## CWD

```{r CWD-QC, child="04_ForestVegCWDQC.Rmd"}
```

## Trees

```{r Tree-QC, child="05_ForestVegTreeQC.Rmd"}
```


## Saplings

```{r Sapling-QC, child="06_ForestVegSaplingQC.Rmd"}
```

## Stems

```{r Stem-QC, child="07_ForestVegStemQC.Rmd"}
```


## Shrubs

```{r Shrub-QC, child="08_ForestVegShrubQC.Rmd"}
```

## Conditions

```{r Condition-QC, child="09_ForestVegConditionsQC.Rmd"}
```

## Foliage

```{r Foliage-QC, child="10_ForestVegFoliageConditionsQC.Rmd"}
```

## Vines

```{r Vine-QC, child="11_ForestVegVineQC.Rmd"}
```


## Quadrats

```{r Quad-QC, child="12_ForestVegQuadsQC.Rmd"}
```


## Seedlings

```{r Seedling-QC, child="13_ForestVegSeedlingQC.Rmd"}
```

## Understory Plants

```{r Herb-QC, child="14_ForestVegHerbQC.Rmd"}
```

## Tags

```{r Tag-QC, child="15_ForestVegTagsQC.Rmd"}
```

## Species

```{r Species-QC, child="16_CommonNamesQC.Rmd"}
```

