---
title: "Forest Vegetation Tree QC"
author: "John Paul Schmit"
date: "5/19/2020"
output: html_document
---


```{r shrub_setup, include=F}
TotShrubs<-nrow(QCShrubs) #Total Number of tree records checked

## Units

# 8.1.0
Shrubs_Bad_Unit<-QCShrubs %>% 
 filter(!Unit_Code %in% c("ANTI", "CATO", "CHOH", "GWMP", "HAFE", "MANA", "MONO", "NACE", "PRWI", "ROCR", "WOTR")) %>% 
 select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name)
  
Shrubs_Bad_Unit_Group<-QCShrubs %>% 
 filter(!Unit_Group %in% c("ANTI","BOHE", "BRUN", "CATO", "CUMB", "GREE", "LOHE", "MAHE", "MANA", "MONO", "NACE", "PISC", "POGO","PRWI", "ROCR", 
                        "SHHI","SHIS","TIDE", "WILL", "WOTR")) %>% 
 select(Unit_Code, Unit_Group, Plot_Name,Sample_Year, Tag, Latin_Name)
  
Shrubs_Mismatch_Unit_Group<-QCShrubs %>% 
   filter(Unit_Code=="ANTI" & Unit_Group!="ANTI"|
          Unit_Code=="CATO" & Unit_Group !="CATO"|
          Unit_Code=="CHOH" & !Unit_Group %in% c("BRUN", "CUMB", "POGO", "WILL") |
          Unit_Code =="GWMP" & !Unit_Group %in% c("POGO","TIDE") |
          Unit_Code =="HAFE" & !Unit_Group %in% c("BOHE", "LOHE", "MAHE","SHHI", "SHIS")|
          Unit_Code=="MANA" & Unit_Group !="MANA" |
          Unit_Code=="MONO" & Unit_Group !="MONO" |
          Unit_Code=="NACE" & !Unit_Group %in% c("GREE","NACE","PISC")|
          Unit_Code=="PRWI" & Unit_Group !="PRWI" |
          Unit_Code=="ROCR" & Unit_Group !="ROCR" |
          Unit_Code=="WOTR" & Unit_Group!="WOTR"
          ) %>% 
     select(Plot_Name, Unit_Code, Unit_Group, Sample_Year, Tag, Latin_Name)

## Plots

#8.2.0
 Shrubs_No_Plot_Name<-QCShrubs %>% 
    filter(is.na(Plot_Name) | Plot_Name=="") %>% 
    select(Unit_Code, Plot_Name,Sample_Year, Tag, Latin_Name)
  
## Panel Frame Cycle  
 
#8.3.0
Shrubs_Bad_Panel<-QCShrubs %>%
 filter(!Panel %in% 1:4) %>% 
 select(Unit_Code, Plot_Name, Sample_Year, Panel,Tag, Latin_Name)
 
#8.4.0
Shrubs_Bad_Frame<-QCShrubs %>%
  filter(!Frame %in% c("Park","Region")) %>% 
  select(Unit_Code, Plot_Name, Sample_Year, Frame,Tag, Latin_Name)
  
#8.5.0
Shrubs_Bad_Cycle<-QCShrubs %>% 
  filter(!(Cycle==1 & Sample_Year %in% 2005:2009) &
         !(Cycle==2 & Sample_Year %in% 2010:2013) &
         !(Cycle==3 & Sample_Year %in% 2014:2017) &
         !(Cycle==4 & Sample_Year %in% 2018:2022)) %>% 
  select(Unit_Code,Plot_Name, Sample_Year, Cycle,Tag, Latin_Name)
 
## Dates

#8.6.0
Shrubs_Bad_Date<-QCShrubs %>% 
  filter(!ymd(Date) %in% QCEvents$Event_Date) %>% 
  select(Unit_Code, Plot_Name, Sample_Year, Date, Tag, Latin_Name)
 
#8.7.0
Shrubs_Bad_Year<-QCShrubs %>% 
 filter(Sample_Year != year(ymd(Date))) %>% 
 select(Unit_Code, Plot_Name, Sample_Year,Date, Tag, Latin_Name)

## Shrub Tag
 
#8.8.0
Shrubs_Bad_Tag<-QCShrubs %>% filter(!Tag %in%1:30000) %>%
  select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name)

Shrubs_Duplicate_Tag<-QCShrubs%>% group_by(Cycle,Tag) %>% 
  summarize(Count=n()) %>% filter(Count!=1)

## Microplot

#6.9.0
Shrubs_Bad_Microplot<-QCShrubs %>% filter(!Microplot_Number %in% c(60,180,300)) %>% 
 select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Microplot_Number)

## Latin Name

# 8.10.0
Shrubs_No_Name<-QCShrubs %>% filter(Latin_Name=="") %>%
 select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name)

Shrubs_Many_Names<-QCShrubs %>% group_by(Tag) %>% 
  filter(n_distinct(Latin_Name)!=1)  %>% 
  select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name)

# ## TSN

# 8.11.0
Shrubs_No_TSN<-QCShrubs %>% filter(is.na(TSN) | TSN=="") %>%
  select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, TSN)

Shrubs_Many_TSN<-QCShrubs %>% group_by(Tag) %>% 
 filter(n_distinct(TSN)!=1)  %>% 
 select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, TSN)

## Status
 
#8.12..0
Shrubs_Bad_Status<-QCShrubs %>% filter(!Status %in% c(Live_Status, Dead_Status, Missing_Status, Other_Status) ) %>%
   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status)
  
## Habit

#8.13.0
Shrubs_Bad_Habit<-QCShrubs %>% filter(!Habit=="Shrub") %>% 
  select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Habit) 

## Vigor

#8.14.0
 
Shrubs_Live_Bad_Vigor<-QCShrubs %>% filter(Status %in% Live_Status & 
         ( (Sample_Year<2017 & !is.na(SaplingVigor)) | (Sample_Year >=2017 & is.na(SaplingVigor))  | 
            (Sample_Year >=2017 & !SaplingVigor %in% 0:5))) %>% 
   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, SaplingVigor)
  
Shrubs_Unalive_Bad_Vigor<-QCShrubs %>% filter(!Status %in% Live_Status, !is.na(SaplingVigor)) %>% 
    select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, SaplingVigor)

#8.15.0
 
Shrubs_Bad_Vigor_Class<-QCShrubs %>% filter( (SaplingVigor==0 & !is.na(VigorClass)) |
                                             (SaplingVigor==1 & VigorClass != "Healthy") |
                                             (SaplingVigor==2 & VigorClass !="Light Decline") |
                                             (SaplingVigor==3 & VigorClass !="Moderate Decline") |
                                             (SaplingVigor==4 & VigorClass !="Severe Decline") |
                                             (SaplingVigor==5 & VigorClass !="Functionally Dead") |
                                             (is.na(SaplingVigor) & VigorClass!="") ) %>% 
      select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, SaplingVigor, VigorClass)

#   
# #7.3.0  
#   Shrubs_Anachronistic_Name <-QCShrubs %>% filter(
#     (Sample_Year < 2008 & Latin_Name == "Alnus serrulata") | (Sample_Year < 2008 & Latin_Name == "Castanea pumila") |
#     (Sample_Year < 2016 & Latin_Name == "Cephalanthus occidentalis") | (Sample_Year < 2008 & Latin_Name == "Cornus amomum") |
#     (Sample_Year < 2007 & Latin_Name == "Euonymus americanus") | (Sample_Year < 2007 & Latin_Name == "Euonumus atropurpureus") |
#     (Sample_Year < 2008 & Latin_Name == "Ligustrum ovalifolium") | (Sample_Year < 2014 & Latin_Name == "Ligustrum sinense") |
#     (Sample_Year < 2008 & Latin_Name == "Ligustrum vulgare") | (Sample_Year < 2008 & Latin_Name == "Lonicera morrowii") |
#     (Sample_Year < 2014 & Latin_Name == "Mahonia bealei") |  (Sample_Year < 2014 & Latin_Name == "Quercus ilicifolia") |
#     (Sample_Year < 2007 & Latin_Name == "Rhododendron periclymenoides") | (Sample_Year < 2014 & Latin_Name == "Rhodotypos scandens") |
#     (Sample_Year < 2008 & Latin_Name == "Rhus copallina") | (Sample_Year < 2008 & Latin_Name == "Sambucus canadensis") |
#     (Sample_Year < 2007 & Latin_Name == "Sambucus pubens") | (Sample_Year < 2014 & Latin_Name == "Spiraea japonica") |
#     (Sample_Year < 2013 & Latin_Name == "Vaccinium stamineum") | (Sample_Year < 2013 & Latin_Name == "Viburnum dilatatum") |
#     (Sample_Year < 2007 & Latin_Name == "Viburnum plicatum") | (Sample_Year < 2007 & Latin_Name == "Viburnum prunifolium") |
#     (Sample_Year < 2014 & Latin_Name == "Viburnum recognitum") | (Sample_Year < 2007 & Latin_Name == "Viburnum sieboldii") |
#     (Sample_Year > 2009 & Latin_Name == "Gaylussacia frondosa") | (Sample_Year > 2009 & Latin_Name == "Rosa carolina") |
#     (Sample_Year > 2009 & Latin_Name == "Rubus argutus") | (Sample_Year > 2009 & Latin_Name == "Symphoricarpos orbiculatus") |
#     (Sample_Year < 2014 & Latin_Name == "Viburnum acerifolium") | (Sample_Year > 2014 & Latin_Name == "Ilex verticillata") |
#     (Sample_Year > 2014 & Latin_Name == "Lindera benzoin") | (Sample_Year > 2014 & Latin_Name == "Kalmia latifolia")
#   ) %>% 
#     select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status)
#   
#
  ## Foliage
# Saplings_Bad_Foliage_Condition<-QCFoliage %>% filter(Sample_Year  %in% QCYears & (is.na(Condition_Description) | 
#               !Condition_Description %in% c("Chlorosis","Holes","Necrosis","Small leaves","Wilting","Other") )) %>% 
#   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Condition_Description, Percent_Afflicted)
#   
# 
# Trees_Bad_Foliage_Percent<-QCFoliage %>% filter(Sample_Year  %in% QCYears & (is.na(Percent_Afflicted) | 
#                             Percent_Afflicted<1 |Percent_Afflicted>100)) %>% 
#     select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Condition_Description, Percent_Afflicted)
# 
# Trees_Unalive_Foliage<- QCFoliage %>% filter(Sample_Year %in% QCYears & !Status %in% Live_Status ) %>% 
#     select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Condition_Description, Percent_Afflicted)


## Tree Conditions
# Trees_Live_Bad_Tree_Condition<-QCConditions %>% filter( (Sample_Year %in% QCYears) & !Pest & (Status %in% Live_Status) &
#   !Condition %in% c("Advanced decay", "Primary branch broken",  "Large dead branches", "Lightning Damage", "Wind Damage", "Buck Rub", "Bark Damage",
#                     "Beaver Damage", "Human Damage", "Mammal Damage", "Bird Damage", "Exposed roots", "Epicormic sprouts", "Fungus", "Fire", "Hollow",
#                     "Sparse foliage", "Open wound", "Vines in the crown",  "Vine stress", "Other visible condition", "Other visible damage")) %>% 
#   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Condition)
# 
# Trees_Live_Anachronistic_Tree_Conditions<-QCConditions %>% filter( (Sample_Year %in% QCYears) & !Pest & (Status %in% Live_Status) &
#       (
#         (Condition =="Lightning Damage" & Sample_Year< 2009) | 
#           (Condition %in% c("Buck Rub", "Bark Damage", "Human Damage") & Sample_Year < 2014) |
#           (Condition =="Beaver Damage" & !Sample_Year %in% 2014:2016) |
#           (Condition =="Epicormic Sprouts" & Sample_Year< 2015) |
#           (Condition %in% c("Mammal Damage", "Bird Damage", "Exposed roots", "Fungus", "Fire", "Hollow", "Sparse foliage",
#                             "Other visible condition") & Sample_Year < 2017) |
#           (Condition =="Vine Stress" & Sample_Year< 2015) |
#          (Condition =="Other visible damage" & Sample_Year> 2016)
#         )) %>%   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Condition)
# 
# 
# Trees_Unalive_Tree_Conditions<-QCConditions %>% filter( (Sample_Year %in% QCYears) & !Pest & 
#                 (Status %in% c(Dead_Status, Missing_Status, Other_Status))) %>% 
#   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Condition)

## Tree Pests

# Trees_Live_Bad_Pest<-QCConditions %>% filter( (Sample_Year %in% QCYears) & Pest & (Status %in% Live_Status) &
#   !Condition %in% c("Asian longhorned beetle", "Beech bark disease",  "Butternut canker", "Chestnut blight", "Dogwood anthracnose", 
#                     "Emerald ash borer", "Gypsy moth","Hemlock Scale", "Hemlock wooly adelgid", "Oak wilt", "Spotted lanternfly", 
#                     "Thousand cankers disease", "Tent caterpillars", "Other significant insect damage")) %>% 
#   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Condition)
# 
# Trees_Live_Anachronistic_Pest<-QCConditions %>% filter( (Sample_Year %in% QCYears) & Pest & (Status %in% Live_Status) &
#       (
#         (Condition %in% c("Dogwood anthracnose","Hemlock Scale") & Sample_Year< 2008) | 
#           (Condition =="Emrerald ash borer" & Sample_Year < 2009) |
#           (Condition %in% c("Asian longhotnrf beetle","Chestnut blight", "Oak wilt", "Thousand cankers disease") & Sample_Year < 2014) |
#           (Condition =="Tent caterpillars" & Sample_Year< 2017) |
#           (Condition =="Spotted lanternfly" & Sample_Year < 2018))
#     ) %>%   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Condition)
# 
# 
# Trees_Unalive_Pest<-QCConditions %>% filter( (Sample_Year %in% QCYears) & Pest & 
#                 (Status %in% c(Dead_Status, Missing_Status, Other_Status))) %>% 
#   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Condition)
# 
# Trees_Pest_Bad_Host<-QCConditions %>% filter((Sample_Year %in% QCYears) & Pest & 
#   (
#    (Condition == "Beach bark disease" & Latin_Name !="Fagus grandifolia") |
#     (Condition =="Butternut canker" & Latin_Name != "Junglans cinerea") |
#     (Condition == "Chestnut blight" & Latin_Name != "Castanea dentata") |
#     (Condition == "Dogwood anthracnose" & Latin_Name != "Cornus florida") |
#     (Condition =="Emerald ash borer" & !Latin_Name %in% c("Fraxinus americana", "Fraxinus nigra", "Fraxinus pennsylvanica", "Fraxinus profunda")) |
#     (Condition %in% c("Hemlock Scale", "Hemlock wooly adelgid") & Latin_Name != "Tsuga canadensis") |
#     (Condition =="Thousand cankers disease" & Latin_Name !="Juglans nigra")
#   )) %>% select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Condition)
# 
# Trees_Bad_Vines<-QCConditions %>% filter(Condition=="Vines in the crown")%>% 
#   left_join(QCVines %>% select(Plot_Name,Sample_Year,Tag=Host_Tag, Vine= Latin_Name )) %>% 
#   filter(is.na(Vine) | Vine=="") %>% 
#   select(Unit_Code, Plot_Name, Sample_Year, Tag, Status,  Condition, Vine)
 
 
#  ## Shrub Browse
#  #sh1
#   Shrubs_Live_Bad_Browsable<-QCShrubs %>% filter(Status %in% Live_Status & !Browsable %in% c("Yes","No", "unk") ) %>% 
#     select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Browsable, Browsed)
# 
#   #sh2  
#   Shrubs_Live_Anachronistic_Browsable<-QCShrubs %>% filter(Status %in% Live_Status & Sample_Year<2010 & Browsable != "unk" ) %>% 
#     select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Browsable, Browsed)
#   
#   #sh3
#   Shrubs_Unalive_Browsable<-QCShrubs %>% filter(!Status %in% Live_Status & Browsable !="" ) %>% 
#     select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Browsable, Browsed)
# 
# #sh4  
#   Shrubs_Live_Bad_Browsed<-QCShrubs %>% filter(Status %in% Live_Status & !Browsed %in% c("Yes","No") ) %>% 
#     select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Browsable, Browsed)
#   
#   #sh5
#   Shrubs_Unalive_Browsed<-QCShrubs %>% filter(!Status %in% Live_Status & Browsed !="" ) %>% 
#     select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Browsable, Browsed)
# #sh6
#   Shrubs_Live_Illogical_Browse <- QCShrubs %>% filter(Status %in% Live_Status, Browsed =="Yes", Browsable == "No") %>% 
#    select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Browsable, Browsed)
#   
# 
# 
# ### Multi-Year Checks
#  
#   Repeat_Shrubs<-QCShrubs %>% group_by(Tag) %>% summarize(Records=n()) %>% filter(Records>1) %>% pull(Tag)
#  
# ##Status  Change 
# 
# #sh7
#   Shrubs_Start_Wrong<-if(length(Repeat_Shrubs>0)){
#     QCShrubs %>% filter(Tag %in% Repeat_Shrubs) %>%
#     group_by(Tag) %>% arrange(Tag, Sample_Year) %>%
#     filter(any(Sample_Year==min(Sample_Year) & (Status  %in% c(Missing_Status, Other_Status, Dead_Status)) |
#            (Status %in% Dead_Status & Sample_Year < 2010 )) ) %>%
#     mutate(Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#     select(Plot_Name, Cycle, Tag, Latin_Name, Status, Start_Year) %>%
#       pivot_wider(id_cols=c(Plot_Name, Tag, Latin_Name, Start_Year) , names_from = Cycle,
#                 names_prefix = "Cycle ", values_from = Status)} else data.frame()
# #sh8
#   Shrubs_Dead_Plus<-if(length(Repeat_Shrubs>0)){
#     QCShrubs %>% filter(Tag %in% Repeat_Shrubs) %>%
#     group_by(Tag) %>% arrange(Tag, Sample_Year) %>%
#     filter(any(Sample_Year!=max(Sample_Year) & Status %in% Dead_Status)) %>%
#     mutate(Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#     select(Plot_Name, Cycle, Sample_Year, Tag, Latin_Name, Status, Start_Year) %>%
#     pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = Status, names_from = Cycle )
#      } else data.frame()
# 
#   #sh9
#  Shrubs_Levitated<-if(length(Repeat_Shrubs>0)){
#    QCShrubs %>% filter(Tag %in% Repeat_Shrubs) %>%
#    group_by(Tag) %>% arrange(Tag, Sample_Year) %>%
#    filter(any(Status =="Alive Fallen" & lead(Status, order_by=Sample_Year) %in% c("Alive Broken", "Alive Leaning",
#             "Alive Standing","Dead Leaning", "Dead Standing"))) %>%
#    mutate(Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#     select(Plot_Name, Cycle, Sample_Year, Tag, Latin_Name, Status, Start_Year) %>%
#     pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = Status, names_from = Cycle ) } else data.frame()
#  
#  #sh10
#  Shrubs_Found_Alive<-if(length(Repeat_Shrubs>0)){
#    QCShrubs %>% filter(Tag %in% Repeat_Shrubs) %>%
#    group_by(Tag) %>% arrange(Tag, Sample_Year) %>%
#    filter(any( (Status %in% Missing_Status) & (lead(Status, order_by=Sample_Year) %in% Live_Status) )) %>%
#    mutate(Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#     select(Plot_Name, Cycle, Sample_Year, Tag, Latin_Name, Status, Start_Year) %>%
#     pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = Status, names_from = Cycle ) } else data.frame()
#  #sh11
#  Shrubs_Downgraded_Persisting <-if(length(Repeat_Shrubs>0)){
#    QCShrubs %>% filter(Tag %in% Repeat_Shrubs) %>%
#    group_by(Tag) %>% arrange(Tag, Sample_Year) %>%
#    filter(any( (Status =="Downgraded to Non-Sampled") & (lead(Status, order_by=Sample_Year) %in%
#                             c(Live_Status, Dead_Status, Other_Status, Missing_Status)) )) %>%
#    mutate(Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#     select(Plot_Name, Cycle, Sample_Year, Tag, Latin_Name, Status, Start_Year) %>%
#     pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = Status, names_from = Cycle ) } else data.frame()
#  #sh12
#   Shrubs_Triple_Missing <-if(length(Repeat_Shrubs>0)){
#     QCShrubs %>% filter(Tag %in% Repeat_Shrubs) %>%
#     group_by(Tag) %>% arrange(Tag, Sample_Year) %>%
#     mutate(Start_Year=min(Sample_Year)) %>%
#     filter(any( (Status %in% Missing_Status) & (lead(Status, order_by=Sample_Year) %in% Missing_Status)
#                 & (lead(Status,n=2, order_by=Sample_Year) %in% Missing_Status))) %>%
#      arrange(Sample_Year) %>%
#      select(Plot_Name, Cycle, Sample_Year, Tag, Latin_Name, Status, Start_Year) %>%
#      pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                  values_from = Status, names_from = Cycle ) } else data.frame()
# 
#  ## Vigor Change
#  
# #sh13
#   Shrubs_Vigor_Jump <-if(length(Repeat_Shrubs>0)){
#     QCShrubs %>% filter(Tag %in% Repeat_Shrubs) %>%
#     group_by(Tag) %>% arrange(Tag, Sample_Year) %>%
#    mutate(Start_Year=min(Sample_Year)) %>%
#     filter(any(
#       (VigorClass =="Moderate Decline" & lead(Status, order_by=Sample_Year) == "Healthy") |
#       (VigorClass =="Functionally Dead" & lead(Status, order_by=Sample_Year) %in% c("Healthy", "Light Decline"))
#       )) %>%
#      arrange(Sample_Year) %>%
#      select(Plot_Name, Cycle, Sample_Year, Tag, Latin_Name, VigorClass, Start_Year) %>%
#      pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                  values_from = VigorClass, names_from = Cycle ) } else data.frame()


## Shrub Condition Change
  
 # Saplings_Lose_EAB<- if(length(Repeat_Saplings>0)){
 #   QCSaplings %>% select(Plot_Name, Tag, Latin_Name, Sample_Year, Cycle, Status) %>% 
 #     left_join(QCConditions %>% filter(Condition=="Emerald ash borer") %>%  select(Tag, Sample_Year, Condition), by=c("Tag", "Sample_Year") ) %>% 
#   filter(Tag %in% Repeat_Trees) %>% mutate(Condition=replace_na(Condition, "None")) %>% 
#   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
#   filter(any (Condition=="Emerald ash borer" & (lead(Condition, order_by = Sample_Year) != "Emerald ash borer")  )) %>% 
#   {if(nrow(.)>0) mutate(., Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#   select(Plot_Name, Cycle, Start_Year, Sample_Year, Tag, Latin_Name, Condition) %>% 
#   pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = c(Condition), names_from = Cycle, names_sep = " " ) else data.frame()} } else data.frame()
#  
# 
# Trees_Lose_Anthracnose<- if(length(Repeat_Trees>0)){
#   QCTrees %>% select(Plot_Name, Tag, Latin_Name, Sample_Year, Cycle, Status) %>% 
#     left_join(QCConditions %>% filter(Condition=="Dogwood anthracnose") %>%  select(Tag, Sample_Year, Condition), by=c("Tag", "Sample_Year") ) %>% 
#   filter(Tag %in% Repeat_Trees) %>% mutate(Condition=replace_na(Condition, "None")) %>% 
#   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
#   filter(any (Condition=="Dogwood anthracnose" & (lead(Condition, order_by = Sample_Year) != "Dogwood anthracnose") & 
#                 lead(Status %in% Live_Status) )) %>% 
#   {if(nrow(.)>0) mutate(., Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#   select(Plot_Name, Cycle, Start_Year, Sample_Year, Tag, Latin_Name, Condition) %>% 
#   pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = c(Condition), names_from = Cycle, names_sep = " " ) else data.frame()} } else data.frame()
# 
# Trees_Lose_Scale <-if(length(Repeat_Trees>0)){
#   QCTrees %>% select(Plot_Name, Tag, Latin_Name, Sample_Year, Cycle, Status) %>% 
#     left_join(QCConditions %>% filter(Condition=="Hemlock Scale") %>%  select(Tag, Sample_Year, Condition), by=c("Tag", "Sample_Year") ) %>% 
#   filter(Tag %in% Repeat_Trees) %>% mutate(Condition=replace_na(Condition, "None")) %>% 
#   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
#   filter(any (Condition=="Hemlock Scale" & (lead(Condition, order_by = Sample_Year) != "Hemlock Scale") & 
#                 lead(Status %in% Live_Status) )) %>% 
#   {if(nrow(.)>0) mutate(., Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#   select(Plot_Name, Cycle, Start_Year, Sample_Year, Tag, Latin_Name, Condition) %>% 
#   pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = c(Condition), names_from = Cycle, names_sep = " " ) else data.frame()} } else data.frame()
#  
# Trees_Lose_Adelgid <-if(length(Repeat_Trees>0)){
#   QCTrees %>% select(Plot_Name, Tag, Latin_Name, Sample_Year, Cycle, Status) %>% 
#     left_join(QCConditions %>% filter(Condition=="Hemlock wooly adelgid") %>%  select(Tag, Sample_Year, Condition), by=c("Tag", "Sample_Year") ) %>% 
#   filter(Tag %in% Repeat_Trees) %>% mutate(Condition=replace_na(Condition, "None")) %>% 
#   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
#   filter(any (Condition=="Hemlock wooly adelgid" & (lead(Condition, order_by = Sample_Year) != "Hemlock wooly adelgid") & 
#                 lead(Status %in% Live_Status) )) %>% 
#   {if(nrow(.)>0) mutate(., Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#   select(Plot_Name, Cycle, Start_Year, Sample_Year, Tag, Latin_Name, Condition) %>% 
#   pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = c(Condition), names_from = Cycle, names_sep = " " ) else data.frame()} } else data.frame()
# 
# 
# Trees_Lose_ExpRoots<- if(length(Repeat_Trees>0)){
#   QCTrees %>% select(Plot_Name, Tag, Latin_Name, Sample_Year, Cycle, Status) %>% 
#     left_join(QCConditions %>% filter(Condition=="Exposed roots") %>%  select(Tag, Sample_Year, Condition), by=c("Tag", "Sample_Year") ) %>% 
#   filter(Tag %in% Repeat_Trees) %>% mutate(Condition=replace_na(Condition, "None")) %>% 
#   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
#   filter(any (Condition=="Exposed roots" & (lead(Condition, order_by = Sample_Year) != "Exposed roots") & 
#                 lead(Status %in% Live_Status) )) %>% 
#   {if(nrow(.)>0) mutate(., Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#   select(Plot_Name, Cycle, Start_Year, Sample_Year, Tag, Latin_Name, Condition) %>% 
#   pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = c(Condition), names_from = Cycle, names_sep = " " ) else data.frame()} } else data.frame()
# 
# Trees_Lose_Hollow<- if(length(Repeat_Trees>0)){
#   QCTrees %>% select(Plot_Name, Tag, Latin_Name, Sample_Year, Cycle, Status) %>% 
#     left_join(QCConditions %>% filter(Condition=="Hollow") %>%  select(Tag, Sample_Year, Condition), by=c("Tag", "Sample_Year") ) %>% 
#   filter(Tag %in% Repeat_Trees) %>% mutate(Condition=replace_na(Condition, "None")) %>% 
#   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
#   filter(any (Condition=="Hollow" & (lead(Condition, order_by = Sample_Year) != "Hollow") & 
#                 lead(Status %in% Live_Status) )) %>% 
#   {if(nrow(.)>0) mutate(., Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#   select(Plot_Name, Cycle, Start_Year, Sample_Year, Tag, Latin_Name, Condition) %>% 
#   pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = c(Condition), names_from = Cycle, names_sep = " " ) else data.frame()} } else data.frame()
#  
# Trees_Lose_Vine_Crown<- if(length(Repeat_Trees>0)){
#   QCTrees %>% select(Plot_Name, Tag, Latin_Name, Sample_Year, Cycle, Status) %>% 
#     left_join(QCConditions %>% filter(Condition=="Vines in the crown") %>%  select(Tag, Sample_Year, Condition), by=c("Tag", "Sample_Year") ) %>% 
#   filter(Tag %in% Repeat_Trees) %>% mutate(Condition=replace_na(Condition, "None")) %>% 
#   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
#   filter(any (Condition=="Vines in the crown" & (lead(Condition, order_by = Sample_Year) != "Vines in the crown") & 
#                 lead(Status %in% Live_Status) )) %>% 
#   {if(nrow(.)>0) mutate(., Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#   select(Plot_Name, Cycle, Start_Year, Sample_Year, Tag, Latin_Name, Condition) %>% 
#   pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = c(Condition), names_from = Cycle, names_sep = " " ) else data.frame()} } else data.frame()
#  
# Trees_Lose_Vine_Stress<- if(length(Repeat_Trees>0)){
#   QCTrees %>% select(Plot_Name, Tag, Latin_Name, Sample_Year, Cycle, Status) %>% 
#     left_join(QCConditions %>% filter(Condition=="Vine stress") %>%  select(Tag, Sample_Year, Condition), by=c("Tag", "Sample_Year") ) %>% 
#   filter(Tag %in% Repeat_Trees) %>% mutate(Condition=replace_na(Condition, "None")) %>% 
#   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
#   filter(any (Condition=="Vine stress" & (lead(Condition, order_by = Sample_Year) != "Vine stress") & 
#                 lead(Status %in% Live_Status) )) %>% 
#   {if(nrow(.)>0) mutate(., Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#   select(Plot_Name, Cycle, Start_Year, Sample_Year, Tag, Latin_Name, Condition) %>% 
#   pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = c(Condition), names_from = Cycle, names_sep = " " ) else data.frame()} } else data.frame()
# 
# Trees_Change_Conditon_Number<-if(length(Repeat_Trees>0)){
#  QCTrees %>% select(Plot_Name, Tag, Latin_Name, Sample_Year,Cycle, Status) %>% 
#     filter(Tag %in% Repeat_Trees) %>% 
#     left_join( QCConditions %>% select(Tag, Sample_Year, Condition) %>% filter(Condition !="") %>% group_by(Tag, Sample_Year) %>% 
#                  summarise(Condition_Total=n()), by=c("Tag","Sample_Year")) %>% mutate(Condition_Total = replace_na(Condition_Total ,0)) %>% 
#     arrange(Tag, Sample_Year) %>% group_by(Tag) %>% 
#     filter(any( Condition_Total!=lead(Condition_Total, order_by = Sample_Year)& lead(Status, order_by = Sample_Year)%in% Live_Status )) %>% 
#     {if(nrow(.)>0) mutate(., Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#   select(Plot_Name, Cycle, Start_Year, Sample_Year, Tag, Latin_Name, Condition_Total) %>% 
#   pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = c(Condition_Total), names_from = Cycle, names_sep = " " ) else data.frame()} } else data.frame()


  
```

- how do we check removed from study?


#### **Shrubs Checked:** `r TotShrubs` ####


### Unit Codes

```{r Shrub_Unit_Codes, echo=FALSE, hold=FALSE, results="asis"}
if(nrow(Shrubs_Bad_Unit)==0) cat("All shrubs have a recognized Unit Code.<br>") else {
   cat(errortext("Shrubs with a missing or unrecongized Unit Code:")); NiceTable(Shrubs_Bad_Unit)}
  
if(nrow(Shrubs_Bad_Unit_Group)==0) cat("All shrubs have a recognized Unit Group.<br>") else {
 cat( errortext("Shrubs with a missing or unrecongized Unit Group:")); NiceTable(Shrubs_Bad_Unit_Group)}
 
if(nrow(Shrubs_Mismatch_Unit_Group)==0) cat("All shrubs have a Unit Group that is consistent with their Unit Code.<br>") else {
    cat(errortext("Shrubs with a Unit Group that is inconsistent with their Unit Code:")); NiceTable(Shrubs_Mismatch_Unit_Group)}

```

---

### Plot Names

```{r Shrub_plot_names, echo=FALSE, hold=FALSE, results="asis"}
if(nrow(Shrubs_No_Plot_Name)==0) cat("All shrubs have a Plot Name.<br>") else {
 errortext("Shrubs with a missing Plot Name:"); NiceTable(Shrubs_No_Plot_Name)}
```

---

### Event Panel, Frame and Cycle

```{r Shrub_Panel_Frame_Cycle,echo=FALSE, hold=FALSE, results="asis"}
 
cat("<br>**Shrub Panel Data**<br>")
if(nrow(Shrubs_Bad_Panel)==0) cat("Each shrub has a panel code from 1 to 4.<br>") else {
errorText("Shrubs without a panel code from 1-4:"); NiceTable(Shrubs_Bad_Panel)}

cat("<br>**Shrub Frame Data**<br>")
if(nrow(Shrubs_Bad_Frame)==0) cat("Each shrub has a frame that is either Region or Park.<br>") else {
errorText("Shrubs without a frame of either Region or Park:"); NiceTable(Shrubs_Bad_Frame)}

cat("<br>**Shrub Cycle Data**<br>")
if(nrow(Shrubs_Bad_Cycle)==0) cat("Each shrub is from a cycle that matches its event year <br>") else {
errorText("Shrubs without a cycle or with a cycle that does not match its event year:"); NiceTable(Shrubs_Bad_Cycle)}

```

---

###  Dates
```{r Shrub_Dates, echo=FALSE, hold=FALSE, results="asis"}

if(nrow(Shrubs_Bad_Date)==0) cat("All shrub dates match an event date.<br>") else {
 errorText("Shrubs whose date does not match an event date:"); NiceTable(Shrubs_Bad_Date)}

if(nrow(Shrubs_Bad_Year)==0) cat("All shrub dates and sample years are consistent.<br>") else {
 errorText("Shrubs whose date does not match its sample year:"); NiceTable(Shrubs_Bad_Year)}

```

---

### Tag

```{r Shrub_Tag, echo=FALSE, hold=FALSE, results="asis"}
 
if(nrow(Shrubs_Bad_Tag)==0) cat("All shrub records have a valid tag.<br>") else {
    errorText("Shrub records with no tag or a tag <1 or >30,000 tag:"); NiceTable(Shrubs_Bad_Tag)}

if(nrow(Shrubs_Duplicate_Tag)==0) cat("No tags are duplicated in a single visit.<br>") else {
  errorText("Shrubs with duplicate tag records:"); NiceTable(Shrubs_Duplicate_Tag)}

```

---

### Microplot

```{r Shrub_Microplot, echo=FALSE, hold=FALSE, results="asis"}
if(nrow(Shrubs_Bad_Microplot)==0) cat("All shrubs have a microplot of 60, 180 or 300.<br>") else {
   errorText("Shrubs with a microplot number that is not 60, 180 or 300:"); NiceTable(Shrubs_Bad_Microplot)}
```

---

### Species ID

```{r Shrub_Species, echo=FALSE, hold=FALSE, results="asis"}
 
if(nrow(Shrubs_No_Name)==0) cat("All shrub records checked have a species ID.<br>") else {
 errorText("Shrubs with no species name:"); NiceTable(Shrubs_No_Name)}

if(nrow(Shrubs_Many_Names)==0) cat("All shrubs have only one species ID.<br>") else {
 errorText("Shrubs with multiple species names:"); NiceTable(Shrubs_Many_Names)}

if(nrow(Shrubs_No_TSN)==0) cat("All shrub records checked have a TSN.<br>") else {
 errorText("Shrubs with no TSN:"); NiceTable(Shrubs_No_TSN)}

if(nrow(Shrubs_Many_TSN)==0) cat("All shrubs have only one TSN.<br>") else {
 errorText("Shrubs with multiple TSB:"); NiceTable(Shrubs_Many_TSN)}

```

---

###  Status
```{r Shrub_Status, echo=FALSE, hold=FALSE, results="asis"}

if(nrow(Shrubs_Bad_Status)==0) cat("All shrub records have a valid status.<br>") else {
  errorText("Shrub records without a status or a status we do not use:"); NiceTable(Shrubs_Bad_Status)}

```

---

### Habit

```{r Shrub_Habit, echo=FALSE, hold=FALSE, results="asis"}

 if(nrow(Shrubs_Bad_Habit)==0) cat("All shrub records have a habit of 'Shrub'.<br>") else {
    errorText("Shrub records without a habit of 'Shrub':"); NiceTable(Shrubs_Bad_Habit)}

```

---

### Vigor

```{r Shrub_vigor, echo=FALSE, hold=FALSE, results="asis"}

cat("<br>**Living Shrubs Vigor Invalid**<br>") 
  if(nrow(Shrubs_Live_Bad_Vigor)==0) cat("All live shrubs have a valid vigor.<br>") else {
   errorText("Living shrub records with a vigor other than 0-5:"); NiceTable(Shrubs_Live_Bad_Vigor)}
 
cat("<br>**Non-Living Shrubs with Vigor**<br>")
  if(nrow(Shrubs_Unalive_Bad_Vigor)==0) cat("No non-living shrubs have a vigor.<br>") else {
     errorText("Non-living shrub records with a vigor:"); NiceTable(Shrubs_Unalive_Bad_Vigor)}

cat("<br>**Shrubs with Inconsistent Vigor and Vigor Class**<br>")
if(nrow(Shrubs_Bad_Vigor_Class)==0) cat("All shrubs have consisntent vigor and vigor classes.<br>") else {
 errorText("Shrubs with inconsistent vigor and vigor classes:"); NiceTable(Shrubs_Bad_Vigor_Class)}

```

---

### Shrub Foliage

Currently checked under Tree Foliage

```{r Shrub_Foliage, echo=FALSE, hold=FALSE, results="asis"}
 
  # if(nrow(Trees_Bad_Foliage_Condition)==0) cat(paste(TotTrees, " Tree records checked and all foliage conditions are valid.  \n")) else {
  #    cat("Living tree records with invalid foliage conditions:  \n"); NiceTable(Trees_Bad_Foliage_Condition)}
  # 
  # if(nrow(Trees_Bad_Foliage_Condition)==0) cat(paste(TotTrees, " Tree records checked and all foliage percents are valid.  \n")) else {
  #    cat("Living tree records with invalid foliage percents:  \n"); NiceTable(Trees_Bad_Foliage_Percent)}
  # 
  # if(nrow(Trees_Unalive_Foliage)==0) cat(paste(TotTrees, " Tree records checked and no non-living trees have foliage condiditons.  \n")) else {
  #    cat("Non-living tree records with foliage conditions:  \n"); NiceTable(Trees_Unalive_Foliage)}
```

---

### Shrub Conditions

Currnetly checked under Tree Conditions

```{r Shrub_Conditions, echo=FALSE, hold=FALSE, results="asis"}
 
# if(nrow(Trees_Live_Bad_Tree_Condition)==0) cat(paste(TotTrees, " Tree records checked and all tree conditions are valid.  \n")) else {
#      cat("Living tree records with a tree condition we don't monitor:  \n"); NiceTable(Trees_Live_Bad_Tree_Condition)}
# 
# if(nrow(Trees_Live_Anachronistic_Tree_Conditions)==0) cat(paste(TotTrees, " Tree records checked and all tree conditions are from the correct year.  \n")) else {cat("Living tree records with a tree condition from the wrong year:  \n"); NiceTable(Trees_Live_Anachronistic_Tree_Conditions)}
# 
# if(nrow(Trees_Unalive_Tree_Conditions)==0) cat(paste(TotTrees, " Tree records checked and all non-living trees have no conditions.  \n")) else { cat("Non-living tree records with a tree condition:  \n"); NiceTable(Trees_Unalive_Tree_Conditions)}
# 
# 
# if(nrow(Trees_Bad_Vines)==0) cat(paste(TotTrees, " Tree records checked and with vines in the crown had vine records.  \n")) else { cat("Tree records with vines in the crown but no corresponding vine record:  \n"); NiceTable(Trees_Bad_Vines)}
```

---

### Shrub Pests

Currently checked under tree pests
```{r Shrub_Pests, echo=FALSE, hold=FALSE, results="asis"}
 
# if(nrow(Trees_Live_Bad_Pest)==0) cat(paste(TotTrees, " Tree records checked and all pest records are valid.  \n")) else {
#      cat("Living tree records with a pest we don't monitor:  \n"); NiceTable(Trees_Live_Bad_Pest)}
#  
#  if(nrow(Trees_Live_Anachronistic_Pest)==0) cat(paste(TotTrees, " Tree records checked and all pests are from the correct year.  \n")) else {cat("Living tree records with a pest from the wrong year:  \n"); NiceTable(Trees_Live_Anachronistic_Pest)}
#  
#  if(nrow(Trees_Unalive_Pest)==0) cat(paste(TotTrees, " Tree records checked and all non-living trees have no pests.  \n")) else {
#    cat("Non-living tree records with a pest:  \n"); NiceTable(Trees_Unalive_Pest)}
# 
#  
#  if(nrow(Trees_Pest_Bad_Host)==0) cat(paste(TotTrees, " Tree records checked and no pests on incorrect host species.  \n")) else {
#    cat("Trees with inconsistent host species - pest pairs:  \n"); NiceTable(Trees_Pest_Bad_Host)}

```

---

### Shrub Browse

```{r Shrub_Browse, echo=FALSE, hold=FALSE, results="asis"}
  
 # cat("<br>**Living Shrubs Browsable Status Invalid**<br>") 
 #   if(nrow(Shrubs_Live_Bad_Browsable)==0) cat("All live shrubs have a valid browsable status.<br>") else {
 #      errorText("Living shrub records with a browsable status other than Yes, No, or unk:"); NiceTable(Shrubs_Live_Bad_Browsable)}
 # 
 # cat("<br>**Living Shrubs Anachronistic Browsable Status**<br>") 
 #   if(nrow(Shrubs_Live_Anachronistic_Browsable)==0) cat("No living shrubs records have a browsable status before 2010.<br>") else {
 #      errorText("Living shrubs records with a browsable status before 2010:"); NiceTable(Shrubs_Live_Anachronistic_Browsable)}
 # 
 #  cat("<br>**Non-Living Shrubs with Browsable Status**<br>")
 #    if(nrow(Shrubs_Unalive_Browsable)==0) cat("No non-living shrubs have a browsable status.<br>") else {
 #       errorText("Non-living shrub records with a browsable status:"); NiceTable(Shrubs_Unalive_Browsable)}
 # 
 #  cat("<br>**Living Shrubs Browsed Status Invalid**<br>") 
 #   if(nrow(Shrubs_Live_Bad_Browsed)==0) cat("All live shrubs have a valid browsed status.<br>") else {
 #      errorText("Living shrub records with a browsed status other than Yes, or No:"); NiceTable(Shrubs_Live_Bad_Browsed)}
 # 
 #  cat("<br>**Non-Living Shrubs with Browsed Status**<br>")
 #    if(nrow(Shrubs_Unalive_Browsed)==0) cat("No non-living shrubs have a browsed status.<br>") else {
 #       errorText("Non-living shrub records with a browsed status:"); NiceTable(Shrubs_Unalive_Browsed)}
 # 
 #   cat("<br>**Living Shrubs with Illogical Browsing**<br>")
 #    if(nrow(Shrubs_Live_Illogical_Browse)==0) cat("No living shrubs have contradictory browsable and browsed status.<br>") else {
 #       errorText("Living shrub records with a browsable status of 'No' and browsed status of'Yes':"); NiceTable(Shrubs_Live_Illogical_Browse)}
 
```

---

### **Change Over Time**

### Shrub Status Discrepancies

```{r Shrub_Status_Change, echo=FALSE, hold=FALSE, results="asis"}
# 
#   cat("<br>**Shrubs that Start in a Non-Sampled Status**<br>")
#    if(nrow(Shrubs_Start_Wrong)==0) cat("No shrubs start as missing downgraded, or dead fallen.<br>") else {
#      errorText("Shrubs that start in a non-sampled status:"); NiceTable(Shrubs_Start_Wrong)}
#  
#   cat("<br>**Shrubs that are Sampled after they are Dead**<br>")
#    if(nrow(Shrubs_Dead_Plus)==0) cat("No shrub was sampled after it was dead.<br>") else {
#      errorText("Shrubs that were reorded as dead and then sampled again:"); NiceTable(Shrubs_Dead_Plus)}
#   
#   cat("<br>**Shrubs that Fell Down and then Levitated Back Up**<br>")
#    if(nrow(Shrubs_Levitated)==0) cat("No shrub was Alive Fallen and then became Standing or Leaning.<br>") else {
#      errorText("Shrubs that were Alive Fallen but then became Standing or Leaning:"); NiceTable(Shrubs_Levitated)}
#   
#   cat("<br>**Shrubs that went Missing and were Found Alive**<br>")
#    if(nrow(Shrubs_Found_Alive)==0) cat("No shrub was Missing and then found Alive.<br>") else {
#      errorText("Shrubs that were Missing but then were found Alive:"); NiceTable(Shrubs_Found_Alive)}
#   
#   cat("<br>**Shrubs that were Downgraded and resampled**<br>")
#    if(nrow(Shrubs_Downgraded_Persisting)==0) cat("No shrub was resampled after being downgraded.<br>") else {
#      errorText("Shrubs that were Downgraded but then were resampled:"); NiceTable(Shrubs_Downgraded_Persisting)}
#   
#  cat("<br>**Shrubs that went Missing Three Times in a Row**<br>")
#    if(nrow(Shrubs_Triple_Missing)==0) cat("No shrub went missing 3 consecutive visits.<br>") else {
#      errorText("Shrubs that were Missing three times in a row:"); NiceTable(Shrubs_Triple_Missing)}

```

---

### Shrub Vigor Change
```{r Shrub_Vigor_Change, echo=FALSE, hold=FALSE, results="asis"}

  # cat("<br>**Shrubs that have a Large Improvement in Vigor**<br>")
  #  if(nrow(Shrubs_Vigor_Jump)==0) cat("No shrub has a 2 class improvement in vigor.<br>") else {
  #    errorText("Shrubs that have a 2 class improvement in vigor:"); NiceTable(Shrubs_Vigor_Jump)}
```


---


### Shrub Condition Change

Currently checked under Tree Condition Change
```{r Shrub_Condition_Change, echo=FALSE, hold=FALSE, results="asis"}

# cat("<br>**Trees that had EAB and then later did not**<br>")
#  if(nrow(Trees_Lose_EAB)==0) cat("No tree had EAB and then lost it.<br>") else {
#    errorText("Trees that had EAB and then lost it:"); NiceTable(Trees_Lose_EAB)}
#
# cat("<br>**Trees that had Dogwood Anthracnose and then later did not**<br>")
#  if(nrow(Trees_Lose_Anthracnose)==0) cat("No tree had Dogwood Anthracnose and then lost it.<br>") else {
#    errorText("Trees that had Dogwood Anthracnose and then lost it:"); NiceTable(Trees_Lose_Anthracnose)}
#
# cat("<br>**Trees that had Hemlock Scale and then later did not**<br>")
#  if(nrow(Trees_Lose_Scale)==0) cat("No tree had Hemlock Scale and then lost it.<br>") else {
#    errorText("Trees that had Hemlock Scale and then lost it:"); NiceTable(Trees_Lose_Scale)}
#
# cat("<br>**Trees that had Hemlock Wooly Adelgid and then later did not**<br>")
#  if(nrow(Trees_Lose_Adelgid)==0) cat("No tree had Hemlock Wooly Adelgid and then lost it.<br>") else {
#    errorText("Trees that had Hemlock Wooly Adelgid and then lost it:"); NiceTable(Trees_Lose_Adelgid)}
#
# cat("<br>**Trees that had exposed roots and then later did not**<br>")
#  if(nrow(Trees_Lose_ExpRoots)==0) cat("No tree had exposed roots and then lost it.<br>") else {
#    errorText("Trees that had exposed roots and then lost it:"); NiceTable(Trees_Lose_ExpRoots)}
#
# cat("<br>**Trees that were hollow and then later were not**<br>")
#  if(nrow(Trees_Lose_Hollow)==0) cat("No tree was hollow and then lost it.<br>") else {
#    errorText("Trees that were hollow and then lost it:"); NiceTable(Trees_Lose_Hollow)}
#
# cat("<br>**Trees that had vines in the crown and then later did not**<br>")
#  if(nrow(Trees_Lose_Vine_Crown)==0) cat("No tree had vines in the crown and then lost it.<br>") else {
#    errorText("Trees that had vines in the crown and then lost it:"); NiceTable(Trees_Lose_Vine_Crown)}
#
# cat("<br>**Trees that had vine stress and then later did not**<br>")
#  if(nrow(Trees_Lose_Vine_Stress)==0) cat("No tree had vine stress and then lost it.<br>") else {
#    errorText("Trees that had vine stress and then lost it:"); NiceTable(Trees_Lose_Vine_Stress)}
#
# cat("<br>**Trees that had changed number of conditions**<br>")
#  if(nrow(Trees_Change_Conditon_Number)==0) cat("No trees changed number of conditions.<br>") else {
#    errorText("Trees that changed number of conditiosn:"); NiceTable(Trees_Change_Conditon_Number)}
```




