---
title: "Forest Vegetation Tree QC"
author: "John Paul Schmit"
date: "5/19/2020"
output: html_document
---


```{r sapling_setup, include=F}
TotSaplings<-nrow(QCSaplings) #Total Number of tree records checked

# Units

# 6.1.0
Saplings_Bad_Unit<-QCSaplings %>% 
  filter(!Unit_Code %in% c("ANTI", "CATO", "CHOH", "GWMP", "HAFE", "MANA", "MONO", "NACE", "PRWI", "ROCR", "WOTR")) %>% 
  select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name)
 
Saplings_Bad_Unit_Group<-QCSaplings %>% 
  filter(!Unit_Group %in% c("ANTI","BOHE", "BRUN", "CATO", "CUMB", "GREE", "LOHE", "MAHE", "MANA", "MONO", "NACE", "PISC", "POGO","PRWI", "ROCR", 
                         "SHHI","SHIS","TIDE", "WILL", "WOTR")) %>% 
  select(Unit_Code, Unit_Group, Plot_Name,Sample_Year, Tag, Latin_Name)
   
Saplings_Mismatch_Unit_Group<-QCSaplings %>% 
    filter(Unit_Code=="ANTI" & Unit_Group!="ANTI"|
           Unit_Code=="CATO" & Unit_Group !="CATO"|
           Unit_Code=="CHOH" & !Unit_Group %in% c("BRUN", "CUMB", "POGO", "WILL") |
           Unit_Code =="GWMP" & !Unit_Group %in% c("POGO","TIDE") |
           Unit_Code =="HAFE" & !Unit_Group %in% c("BOHE", "LOHE", "MAHE","SHHI", "SHIS")|
           Unit_Code=="MANA" & Unit_Group !="MANA" |
           Unit_Code=="MONO" & Unit_Group !="MONO" |
           Unit_Code=="NACE" & !Unit_Group %in% c("GREE","NACE","PISC")|
           Unit_Code=="PRWI" & Unit_Group !="PRWI" |
           Unit_Code=="ROCR" & Unit_Group !="ROCR" |
           Unit_Code=="WOTR" & Unit_Group!="WOTR"
           ) %>% 
      select(Plot_Name, Unit_Code, Unit_Group, Sample_Year, Tag, Latin_Name)
 
## Plots

#6.2.0
  Saplings_No_Plot_Name<-QCSaplings %>% 
     filter(is.na(Plot_Name) | Plot_Name=="") %>% 
     select(Unit_Code, Plot_Name,Sample_Year, Tag, Latin_Name)
   
## Panel Frame Cycle  
  
#6.3.0
Saplings_Bad_Panel<-QCSaplings %>%
  filter(!Panel %in% 1:4) %>% 
  select(Unit_Code, Plot_Name, Sample_Year, Panel,Tag, Latin_Name)
  
#6.4.0
Saplings_Bad_Frame<-QCSaplings %>%
   filter(!Frame %in% c("Park","Region")) %>% 
   select(Unit_Code, Plot_Name, Sample_Year, Frame,Tag, Latin_Name)
   
#6.5.0
Saplings_Bad_Cycle<-QCSaplings %>% 
   filter(!(Cycle==1 & Sample_Year %in% 2005:2009) &
          !(Cycle==2 & Sample_Year %in% 2010:2013) &
          !(Cycle==3 & Sample_Year %in% 2014:2017) &
          !(Cycle==4 & Sample_Year %in% 2018:2022)) %>% 
   select(Unit_Code,Plot_Name, Sample_Year, Cycle,Tag, Latin_Name)

## Dates

#6.6.0
Saplings_Bad_Date<-QCSaplings %>% 
   filter(!ymd(Date) %in% QCEvents$Event_Date) %>% 
   select(Unit_Code, Plot_Name, Sample_Year, Date, Tag, Latin_Name)

  
#6.7.0
Saplings_Bad_Year<-QCSaplings %>% 
 filter(Sample_Year != year(ymd(Date))) %>% 
 select(Unit_Code, Plot_Name, Sample_Year,Date, Tag, Latin_Name)

## Sapling Tag

#6.8.0
Saplings_Bad_Tag<-QCSaplings %>% filter(!Tag %in%1:30000) %>%
   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name)

Saplings_Duplicate_Tag<-QCSaplings %>% group_by(Cycle,Tag) %>% 
   summarize(Count=n()) %>% filter(Count!=1)

## Microplot

#6.9.0
Saplings_Bad_Microplot<-QCSaplings %>% filter(!Microplot_Number %in% c(60,180,300)) %>% 
  select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Microplot_Number)


## Latin Name

# 6.10.0
Saplings_No_Name<-QCSaplings %>% filter(Latin_Name=="") %>%
  select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name)

Saplings_Many_Names<-QCSaplings %>% group_by(Tag) %>% 
 filter(n_distinct(Latin_Name)!=1)  %>% 
 select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name)

## TSN

# 6.11.0
Saplings_No_TSN<-QCSaplings %>% filter(is.na(TSN) | TSN=="") %>%
 select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, TSN)

Saplings_Many_TSN<-QCSaplings %>% group_by(Tag) %>% 
  filter(n_distinct(TSN)!=1)  %>% 
  select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, TSN)

## Stems

#6.12.0
Saplings_Live_Bad_Stems<-QCSaplings %>% filter(Status %in% Live_Status & (is.na(StemsLive)| StemsLive<1 | StemsLive>=6) )  %>% 
    select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, StemsLive)

Saplings_Unalive_Living_Stems<-QCSaplings %>% filter(!Status %in% Live_Status & (is.na(StemsLive) | StemsLive>0))  %>% 
    select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, StemsLive)
 
  
  
  


#6.1.0
Saplings_Bad_Status<-QCSaplings %>% filter(is.na(Status) | !Status %in% c(Live_Status, Dead_Status, Missing_Status, Other_Status) ) %>%
  select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status)


#6.4.0
Saplings_Bad_Habit<-QCSaplings %>% filter(!Habit=="Tree") %>% 
 select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Habit) 



## DBH

#6.7.0
 Saplings_Bad_DBH_Check <-QCSaplings %>% filter( (Sample_Year<2018 & DBH_Check) | 
      (Sample_Year>2017 & DBH_Check & 
          Status %in% c(Missing_Status, "Dead Fallen", "Dead Missing", "Dead - Too Small", Other_Status))) %>% 
    select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, DBH_Check)

 #6.8.0
 Saplings_Live_Bad_DBH<-QCSaplings %>% filter(Status %in% Live_Status & (
    (is.na(Equiv_Live_DBH_cm) | Equiv_Live_DBH_cm < 1 | Equiv_Live_DBH_cm >= 10) ))  %>% 
    select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Equiv_Live_DBH_cm)
 
 #6.9.0
 Saplings_Dead_Bad_DBH<-QCSaplings %>% filter(Status %in% c("Dead Leaning", "Dead Standing") & (
     is.na(Equiv_Live_DBH_cm) | Equiv_Live_DBH_cm>0 ) )  %>% 
    select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Equiv_Live_DBH_cm)
 
 #6.10.0
 Saplings_Other_Bad_DBH<-QCSaplings %>% filter(Status %in% c(Missing_Status, Other_Status, 
     "Dead", "Dead - Human Action", "Dead - Too Small", "Dead Fallen", "Dead Missing") & (
    is.na(Equiv_Live_DBH_cm) | Equiv_Live_DBH_cm!=0 ))  %>% 
    select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Equiv_Live_DBH_cm)
 
 # 6.11.0
 Sapling_Stems_Live_Bad_DBH<-QCStems %>% filter(Sample_Year %in% QCYears, Live==T, Class=="Sapling", (is.na(DBH) | DBH<1 |DBH >=10)) %>% 
   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, DBH, Live )

 #6.12.0
 Sapling_Stems_Dead_Bad_DBH<-QCStems %>% filter(Sample_Year %in% QCYears, Live==F, Class=="Sapling", (is.na(DBH) | DBH<10)) %>% 
   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, DBH, Live )
 
 #6.13.0
  Sapling_Stems_Other_Bad_DBH<-QCStems %>% filter(Sample_Year %in% QCYears, Class=="Sapling", Status %in% c(Missing_Status, Other_Status, 
     "Dead", "Dead - Human Action", "Dead - Too Small", "Dead Fallen", "Dead Missing")) %>% 
   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, DBH, Live )

 ## Vigor
 
#6.14.0
 # Saplings_Live_Bad_Vigor<-QCSaplings %>% filter(Status %in% Live_Status & 
 #       ( (Sample_Year<2017 & !is.na(SaplingVigor)) | (Sample_Year >=2017 & (is.na(SaplingVigor)  | !SaplingVigor %in% 0:5)) )) %>% 
 #    select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, SaplingVigor, VigorClass)
 
#6.15.0  
 # Saplings_Unalive_Bad_Vigor<-QCSaplings %>% filter(!Status %in% Live_Status & !is.na(SaplingVigor)) %>% 
 #    select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, SaplingVigor, VigorClass)
 
 

## Foliage

#6.16.0
# Saplings_Bad_Foliage_Condition<-QCFoliage %>% filter(Sample_Year  %in% QCYears & (is.na(Condition_Description) | 
#               !Condition_Description %in% c("Chlorosis","Holes","Necrosis","Small leaves","Wilting","Other") )) %>% 
#   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Condition_Description, Percent_Afflicted)
#   
# 
# Trees_Bad_Foliage_Percent<-QCFoliage %>% filter(Sample_Year  %in% QCYears & (is.na(Percent_Afflicted) | 
#                             Percent_Afflicted<1 |Percent_Afflicted>100)) %>% 
#     select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Condition_Description, Percent_Afflicted)
# 
# Trees_Unalive_Foliage<- QCFoliage %>% filter(Sample_Year %in% QCYears & !Status %in% Live_Status ) %>% 
#     select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Condition_Description, Percent_Afflicted)


## Tree Conditions
# Trees_Live_Bad_Tree_Condition<-QCConditions %>% filter( (Sample_Year %in% QCYears) & !Pest & (Status %in% Live_Status) &
#   !Condition %in% c("Advanced decay", "Primary branch broken",  "Large dead branches", "Lightning Damage", "Wind Damage", "Buck Rub", "Bark Damage",
#                     "Beaver Damage", "Human Damage", "Mammal Damage", "Bird Damage", "Exposed roots", "Epicormic sprouts", "Fungus", "Fire", "Hollow",
#                     "Sparse foliage", "Open wound", "Vines in the crown",  "Vine stress", "Other visible condition", "Other visible damage")) %>% 
#   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Condition)
# 
# Trees_Live_Anachronistic_Tree_Conditions<-QCConditions %>% filter( (Sample_Year %in% QCYears) & !Pest & (Status %in% Live_Status) &
#       (
#         (Condition =="Lightning Damage" & Sample_Year< 2009) | 
#           (Condition %in% c("Buck Rub", "Bark Damage", "Human Damage") & Sample_Year < 2014) |
#           (Condition =="Beaver Damage" & !Sample_Year %in% 2014:2016) |
#           (Condition =="Epicormic Sprouts" & Sample_Year< 2015) |
#           (Condition %in% c("Mammal Damage", "Bird Damage", "Exposed roots", "Fungus", "Fire", "Hollow", "Sparse foliage",
#                             "Other visible condition") & Sample_Year < 2017) |
#           (Condition =="Vine Stress" & Sample_Year< 2015) |
#          (Condition =="Other visible damage" & Sample_Year> 2016)
#         )) %>%   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Condition)
# 
# 
# Trees_Unalive_Tree_Conditions<-QCConditions %>% filter( (Sample_Year %in% QCYears) & !Pest & 
#                 (Status %in% c(Dead_Status, Missing_Status, Other_Status))) %>% 
#   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Condition)

## Tree Pests

# Trees_Live_Bad_Pest<-QCConditions %>% filter( (Sample_Year %in% QCYears) & Pest & (Status %in% Live_Status) &
#   !Condition %in% c("Asian longhorned beetle", "Beech bark disease",  "Butternut canker", "Chestnut blight", "Dogwood anthracnose", 
#                     "Emerald ash borer", "Gypsy moth","Hemlock Scale", "Hemlock wooly adelgid", "Oak wilt", "Spotted lanternfly", 
#                     "Thousand cankers disease", "Tent caterpillars", "Other significant insect damage")) %>% 
#   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Condition)
# 
# Trees_Live_Anachronistic_Pest<-QCConditions %>% filter( (Sample_Year %in% QCYears) & Pest & (Status %in% Live_Status) &
#       (
#         (Condition %in% c("Dogwood anthracnose","Hemlock Scale") & Sample_Year< 2008) | 
#           (Condition =="Emrerald ash borer" & Sample_Year < 2009) |
#           (Condition %in% c("Asian longhotnrf beetle","Chestnut blight", "Oak wilt", "Thousand cankers disease") & Sample_Year < 2014) |
#           (Condition =="Tent caterpillars" & Sample_Year< 2017) |
#           (Condition =="Spotted lanternfly" & Sample_Year < 2018))
#     ) %>%   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Condition)
# 
# 
# Trees_Unalive_Pest<-QCConditions %>% filter( (Sample_Year %in% QCYears) & Pest & 
#                 (Status %in% c(Dead_Status, Missing_Status, Other_Status))) %>% 
#   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Condition)
# 
# Trees_Pest_Bad_Host<-QCConditions %>% filter((Sample_Year %in% QCYears) & Pest & 
#   (
#    (Condition == "Beach bark disease" & Latin_Name !="Fagus grandifolia") |
#     (Condition =="Butternut canker" & Latin_Name != "Junglans cinerea") |
#     (Condition == "Chestnut blight" & Latin_Name != "Castanea dentata") |
#     (Condition == "Dogwood anthracnose" & Latin_Name != "Cornus florida") |
#     (Condition =="Emerald ash borer" & !Latin_Name %in% c("Fraxinus americana", "Fraxinus nigra", "Fraxinus pennsylvanica", "Fraxinus profunda")) |
#     (Condition %in% c("Hemlock Scale", "Hemlock wooly adelgid") & Latin_Name != "Tsuga canadensis") |
#     (Condition =="Thousand cankers disease" & Latin_Name !="Juglans nigra")
#   )) %>% select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Condition)
# 
# Trees_Bad_Vines<-QCConditions %>% filter(Condition=="Vines in the crown")%>% 
#   left_join(QCVines %>% select(Plot_Name,Sample_Year,Tag=Host_Tag, Vine= Latin_Name )) %>% 
#   filter(is.na(Vine) | Vine=="") %>% 
#   select(Unit_Code, Plot_Name, Sample_Year, Tag, Status,  Condition, Vine)
 
 
 ## Sapling Browse
  
#s1
 Saplings_Live_Bad_Browsable<-QCSaplings %>% filter(Status %in% Live_Status & !Browsable %in% c("Yes","No", "unk") ) %>% 
   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Browsable, Browsed)
 
 #s2
 Saplings_Live_Anachronistic_Browsable<-QCSaplings %>% filter(Status %in% Live_Status & Sample_Year<2010 & Browsable != "unk" ) %>% 
   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Browsable, Browsed)
 
 #s3
 Saplings_Unalive_Browsable<-QCSaplings %>% filter(!Status %in% Live_Status & Browsable !="" ) %>% 
   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Browsable, Browsed)

 #s4
 Saplings_Live_Bad_Browsed<-QCSaplings %>% filter(Status %in% Live_Status & !Browsed %in% c("Yes","No") ) %>% 
   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Browsable, Browsed)
 
 #s5
 Saplings_Unalive_Browsed<-QCSaplings %>% filter(!Status %in% Live_Status & Browsed !="" ) %>% 
   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Browsable, Browsed)
 
 #s6
 Saplings_Live_Illogical_Browse <- QCSaplings %>% filter(Status %in% Live_Status, Browsed =="Yes", Browsable == "No") %>% 
  select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Browsable, Browsed)
 
 ### Multi-Year Checks
 
Repeat_Saplings<-QCSaplings %>% group_by(Tag) %>% summarize(Records=n()) %>% filter(Records>1) %>% pull(Tag)
 
# #Status  Change 

#s7
 Saplings_Start_Wrong<-if(length(Repeat_Saplings>0)){
   QCSaplings %>% filter(Tag %in% Repeat_Saplings) %>% 
   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
   filter(any(Sample_Year==min(Sample_Year) & (Status  %in% c(Missing_Status, Other_Status, Dead_Status)) | 
            (Status %in% Dead_Status & Sample_Year < 2010 )) ) %>% 
   mutate(Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>% 
   select(Plot_Name, Cycle, Tag, Latin_Name, Status, Start_Year) %>% 
     pivot_wider(id_cols=c(Plot_Name, Tag, Latin_Name, Start_Year) , names_from = Cycle, 
                 names_prefix = "Cycle ", values_from = Status)} else data.frame()
 #s8
 Saplings_Dead_Plus<-if(length(Repeat_Saplings>0)){
   QCSaplings %>% filter(Tag %in% Repeat_Saplings) %>% 
   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
   filter(any(Sample_Year!=max(Sample_Year) & Status %in% Dead_Status)) %>% 
   mutate(Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>% 
    select(Plot_Name, Cycle, Sample_Year, Tag, Latin_Name, Status, Start_Year) %>% 
    pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
                values_from = Status, names_from = Cycle )
     } else data.frame()
             
#s9   
 Saplings_Levitated<-if(length(Repeat_Saplings>0)){
   QCSaplings %>% filter(Tag %in% Repeat_Saplings) %>% 
   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
   filter(any(Status =="Alive Fallen" & lead(Status, order_by=Sample_Year) %in% c("Alive Broken", "Alive Leaning", 
            "Alive Standing","Dead Leaning", "Dead Standing"))) %>% 
   mutate(Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>% 
    select(Plot_Name, Cycle, Sample_Year, Tag, Latin_Name, Status, Start_Year) %>% 
    pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
                values_from = Status, names_from = Cycle ) } else data.frame()
 
 #s10
 Saplings_Found_Alive<-if(length(Repeat_Saplings>0)){
   QCSaplings %>% filter(Tag %in% Repeat_Saplings) %>% 
   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
   filter(any( (Status %in% Missing_Status) & (lead(Status, order_by=Sample_Year) %in% Live_Status) )) %>% 
   mutate(Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>% 
    select(Plot_Name, Cycle, Sample_Year, Tag, Latin_Name, Status, Start_Year) %>% 
    pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
                values_from = Status, names_from = Cycle ) } else data.frame()
 
 #s11
 Saplings_Downgraded_Persisting <-if(length(Repeat_Saplings>0)){
   QCSaplings %>% filter(Tag %in% Repeat_Saplings) %>% 
   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
   filter(any( (Status =="Downgraded to Non-Sampled") & (lead(Status, order_by=Sample_Year) %in% 
                            c(Live_Status, Dead_Status, Other_Status, Missing_Status)) )) %>% 
   mutate(Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>% 
    select(Plot_Name, Cycle, Sample_Year, Tag, Latin_Name, Status, Start_Year) %>% 
    pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
                values_from = Status, names_from = Cycle ) } else data.frame()

#s12 
 Saplings_Triple_Missing <-if(length(Repeat_Saplings>0)){
   QCSaplings %>% filter(Tag %in% Repeat_Saplings) %>% 
   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
   mutate(Start_Year=min(Sample_Year)) %>%
   filter(any( (Status %in% Missing_Status) & (lead(Status, order_by=Sample_Year) %in% Missing_Status)
               & (lead(Status,n=2, order_by=Sample_Year) %in% Missing_Status))) %>% 
    arrange(Sample_Year) %>% 
    select(Plot_Name, Cycle, Sample_Year, Tag, Latin_Name, Status, Start_Year) %>% 
    pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
                values_from = Status, names_from = Cycle ) } else data.frame()
 
## Vigor Change
 
 #s13
 Saplings_Vigor_Jump <-if(length(Repeat_Saplings>0)){
   QCSaplings %>% filter(Tag %in% Repeat_Saplings) %>% 
   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
  mutate(Start_Year=min(Sample_Year)) %>%
   filter(any( 
     (VigorClass =="Moderate Decline" & lead(Status, order_by=Sample_Year) == "Healthy") |
     (VigorClass =="Functionally Dead" & lead(Status, order_by=Sample_Year) %in% c("Healthy", "Light Decline"))
     )) %>% 
    arrange(Sample_Year) %>% 
    select(Plot_Name, Cycle, Sample_Year, Tag, Latin_Name, VigorClass, Start_Year) %>% 
    pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
                values_from = VigorClass, names_from = Cycle ) } else data.frame()

## Sapling Diameter Change

 #s14
 Saplings_Live_Large_DBH_change <-if(length(Repeat_Saplings>0)){
   QCSaplings %>% filter(Tag %in% Repeat_Saplings) %>% 
   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
     mutate(Start_Year=min(Sample_Year)) %>% 
   filter(any(Status %in% Live_Status & lead(Status, order_by = Sample_Year) %in% Live_Status & 
           abs(Equiv_Live_DBH_cm -lead(Equiv_Live_DBH_cm, order_by=Sample_Year) > 3))) %>% 
   arrange(Sample_Year) %>% 
    select(Plot_Name, Cycle, Sample_Year, Tag, Latin_Name, LiveDBH=Equiv_Live_DBH_cm, StemsLive, Start_Year) %>% 
    {if(nrow(.)!=0) pivot_wider(.,id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
                values_from = c(StemsLive, LiveDBH), names_from = Cycle, names_sep = " " ) else data.frame()}
   } else data.frame()

#s15 
  Saplings_Start_Too_Large <-if(length(Repeat_Saplings>0)){
   QCSaplings %>% 
   #This next line excludes any tree tag present the first time a plot was sampled
   filter(!Tag %in% (semi_join(QCSaplings, QCEvents %>% group_by(Plot_Name) %>% filter(rank(Event_Year)==1)) %>% pull (Tag)),
      Tag %in% Repeat_Saplings) %>% 
   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
  mutate(Start_Year=min(Sample_Year)) %>%
   filter(any(Status %in% Live_Status &  Equiv_Live_DBH_cm >3 & is.na(lag(Equiv_Live_DBH_cm, order_by = Sample_Year) ))) %>% 
    arrange(Sample_Year) %>% 
   select(Plot_Name, Cycle, Sample_Year, Tag, Latin_Name, LiveDBH=Equiv_Live_DBH_cm, StemsLive, Start_Year) %>% 
   pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
                 values_from = c(StemsLive, LiveDBH), names_from = Cycle, names_sep = " " ) } else data.frame()
 
## Sapling Condition Change
  
 # Saplings_Lose_EAB<- if(length(Repeat_Saplings>0)){
 #   QCSaplings %>% select(Plot_Name, Tag, Latin_Name, Sample_Year, Cycle, Status) %>% 
 #     left_join(QCConditions %>% filter(Condition=="Emerald ash borer") %>%  select(Tag, Sample_Year, Condition), by=c("Tag", "Sample_Year") ) %>% 
#   filter(Tag %in% Repeat_Trees) %>% mutate(Condition=replace_na(Condition, "None")) %>% 
#   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
#   filter(any (Condition=="Emerald ash borer" & (lead(Condition, order_by = Sample_Year) != "Emerald ash borer")  )) %>% 
#   {if(nrow(.)>0) mutate(., Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#   select(Plot_Name, Cycle, Start_Year, Sample_Year, Tag, Latin_Name, Condition) %>% 
#   pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = c(Condition), names_from = Cycle, names_sep = " " ) else data.frame()} } else data.frame()
#  
# 
# Trees_Lose_Anthracnose<- if(length(Repeat_Trees>0)){
#   QCTrees %>% select(Plot_Name, Tag, Latin_Name, Sample_Year, Cycle, Status) %>% 
#     left_join(QCConditions %>% filter(Condition=="Dogwood anthracnose") %>%  select(Tag, Sample_Year, Condition), by=c("Tag", "Sample_Year") ) %>% 
#   filter(Tag %in% Repeat_Trees) %>% mutate(Condition=replace_na(Condition, "None")) %>% 
#   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
#   filter(any (Condition=="Dogwood anthracnose" & (lead(Condition, order_by = Sample_Year) != "Dogwood anthracnose") & 
#                 lead(Status %in% Live_Status) )) %>% 
#   {if(nrow(.)>0) mutate(., Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#   select(Plot_Name, Cycle, Start_Year, Sample_Year, Tag, Latin_Name, Condition) %>% 
#   pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = c(Condition), names_from = Cycle, names_sep = " " ) else data.frame()} } else data.frame()
# 
# Trees_Lose_Scale <-if(length(Repeat_Trees>0)){
#   QCTrees %>% select(Plot_Name, Tag, Latin_Name, Sample_Year, Cycle, Status) %>% 
#     left_join(QCConditions %>% filter(Condition=="Hemlock Scale") %>%  select(Tag, Sample_Year, Condition), by=c("Tag", "Sample_Year") ) %>% 
#   filter(Tag %in% Repeat_Trees) %>% mutate(Condition=replace_na(Condition, "None")) %>% 
#   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
#   filter(any (Condition=="Hemlock Scale" & (lead(Condition, order_by = Sample_Year) != "Hemlock Scale") & 
#                 lead(Status %in% Live_Status) )) %>% 
#   {if(nrow(.)>0) mutate(., Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#   select(Plot_Name, Cycle, Start_Year, Sample_Year, Tag, Latin_Name, Condition) %>% 
#   pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = c(Condition), names_from = Cycle, names_sep = " " ) else data.frame()} } else data.frame()
#  
# Trees_Lose_Adelgid <-if(length(Repeat_Trees>0)){
#   QCTrees %>% select(Plot_Name, Tag, Latin_Name, Sample_Year, Cycle, Status) %>% 
#     left_join(QCConditions %>% filter(Condition=="Hemlock wooly adelgid") %>%  select(Tag, Sample_Year, Condition), by=c("Tag", "Sample_Year") ) %>% 
#   filter(Tag %in% Repeat_Trees) %>% mutate(Condition=replace_na(Condition, "None")) %>% 
#   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
#   filter(any (Condition=="Hemlock wooly adelgid" & (lead(Condition, order_by = Sample_Year) != "Hemlock wooly adelgid") & 
#                 lead(Status %in% Live_Status) )) %>% 
#   {if(nrow(.)>0) mutate(., Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#   select(Plot_Name, Cycle, Start_Year, Sample_Year, Tag, Latin_Name, Condition) %>% 
#   pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = c(Condition), names_from = Cycle, names_sep = " " ) else data.frame()} } else data.frame()
# 
# 
# Trees_Lose_ExpRoots<- if(length(Repeat_Trees>0)){
#   QCTrees %>% select(Plot_Name, Tag, Latin_Name, Sample_Year, Cycle, Status) %>% 
#     left_join(QCConditions %>% filter(Condition=="Exposed roots") %>%  select(Tag, Sample_Year, Condition), by=c("Tag", "Sample_Year") ) %>% 
#   filter(Tag %in% Repeat_Trees) %>% mutate(Condition=replace_na(Condition, "None")) %>% 
#   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
#   filter(any (Condition=="Exposed roots" & (lead(Condition, order_by = Sample_Year) != "Exposed roots") & 
#                 lead(Status %in% Live_Status) )) %>% 
#   {if(nrow(.)>0) mutate(., Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#   select(Plot_Name, Cycle, Start_Year, Sample_Year, Tag, Latin_Name, Condition) %>% 
#   pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = c(Condition), names_from = Cycle, names_sep = " " ) else data.frame()} } else data.frame()
# 
# Trees_Lose_Hollow<- if(length(Repeat_Trees>0)){
#   QCTrees %>% select(Plot_Name, Tag, Latin_Name, Sample_Year, Cycle, Status) %>% 
#     left_join(QCConditions %>% filter(Condition=="Hollow") %>%  select(Tag, Sample_Year, Condition), by=c("Tag", "Sample_Year") ) %>% 
#   filter(Tag %in% Repeat_Trees) %>% mutate(Condition=replace_na(Condition, "None")) %>% 
#   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
#   filter(any (Condition=="Hollow" & (lead(Condition, order_by = Sample_Year) != "Hollow") & 
#                 lead(Status %in% Live_Status) )) %>% 
#   {if(nrow(.)>0) mutate(., Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#   select(Plot_Name, Cycle, Start_Year, Sample_Year, Tag, Latin_Name, Condition) %>% 
#   pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = c(Condition), names_from = Cycle, names_sep = " " ) else data.frame()} } else data.frame()
#  
# Trees_Lose_Vine_Crown<- if(length(Repeat_Trees>0)){
#   QCTrees %>% select(Plot_Name, Tag, Latin_Name, Sample_Year, Cycle, Status) %>% 
#     left_join(QCConditions %>% filter(Condition=="Vines in the crown") %>%  select(Tag, Sample_Year, Condition), by=c("Tag", "Sample_Year") ) %>% 
#   filter(Tag %in% Repeat_Trees) %>% mutate(Condition=replace_na(Condition, "None")) %>% 
#   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
#   filter(any (Condition=="Vines in the crown" & (lead(Condition, order_by = Sample_Year) != "Vines in the crown") & 
#                 lead(Status %in% Live_Status) )) %>% 
#   {if(nrow(.)>0) mutate(., Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#   select(Plot_Name, Cycle, Start_Year, Sample_Year, Tag, Latin_Name, Condition) %>% 
#   pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = c(Condition), names_from = Cycle, names_sep = " " ) else data.frame()} } else data.frame()
#  
# Trees_Lose_Vine_Stress<- if(length(Repeat_Trees>0)){
#   QCTrees %>% select(Plot_Name, Tag, Latin_Name, Sample_Year, Cycle, Status) %>% 
#     left_join(QCConditions %>% filter(Condition=="Vine stress") %>%  select(Tag, Sample_Year, Condition), by=c("Tag", "Sample_Year") ) %>% 
#   filter(Tag %in% Repeat_Trees) %>% mutate(Condition=replace_na(Condition, "None")) %>% 
#   group_by(Tag) %>% arrange(Tag, Sample_Year) %>% 
#   filter(any (Condition=="Vine stress" & (lead(Condition, order_by = Sample_Year) != "Vine stress") & 
#                 lead(Status %in% Live_Status) )) %>% 
#   {if(nrow(.)>0) mutate(., Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#   select(Plot_Name, Cycle, Start_Year, Sample_Year, Tag, Latin_Name, Condition) %>% 
#   pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = c(Condition), names_from = Cycle, names_sep = " " ) else data.frame()} } else data.frame()
# 
# Trees_Change_Conditon_Number<-if(length(Repeat_Trees>0)){
#  QCTrees %>% select(Plot_Name, Tag, Latin_Name, Sample_Year,Cycle, Status) %>% 
#     filter(Tag %in% Repeat_Trees) %>% 
#     left_join( QCConditions %>% select(Tag, Sample_Year, Condition) %>% filter(Condition !="") %>% group_by(Tag, Sample_Year) %>% 
#                  summarise(Condition_Total=n()), by=c("Tag","Sample_Year")) %>% mutate(Condition_Total = replace_na(Condition_Total ,0)) %>% 
#     arrange(Tag, Sample_Year) %>% group_by(Tag) %>% 
#     filter(any( Condition_Total!=lead(Condition_Total, order_by = Sample_Year)& lead(Status, order_by = Sample_Year)%in% Live_Status )) %>% 
#     {if(nrow(.)>0) mutate(., Start_Year=min(Sample_Year)) %>% arrange(Sample_Year) %>%
#   select(Plot_Name, Cycle, Start_Year, Sample_Year, Tag, Latin_Name, Condition_Total) %>% 
#   pivot_wider(id_cols = c(Plot_Name, Tag, Latin_Name, Start_Year), names_prefix = "Cycle ",
#                 values_from = c(Condition_Total), names_from = Cycle, names_sep = " " ) else data.frame()} } else data.frame()


  
```


- Condition checks  other status should not be checked (not sure how EAB works), but only once we started doing this for saplings
- if sapling is listed as live Dead stems should be >=10cm (double check)
- if saplings is listed as dead should not have any dhb's measured
- if saplings is missing should have no stems at all
- Tree foliage condiditons only on living saplings, percent between 1 and 100, condiition should be one of the choices and only once we started with this
- tree conditions only on live trees, except for EAB on dead. never on missing. should be from list that was current. and only once we started with this
- if condition is vines in crown, should have 1 or more vines on it. and only once we stated with this


#### **Saplings Checked:** `r TotSaplings` ####


### Unit Codes

```{r Sapling_Unit_Codes, echo=FALSE, hold=FALSE, results="asis"}
if(nrow(Saplings_Bad_Unit)==0) cat("All saplings have a recognized Unit Code.<br>") else {
    cat(errortext("Trees with a missing or unrecongized Unit Code:")); NiceTable(Saplings_Bad_Unit)}
 
if(nrow(Saplings_Bad_Unit_Group)==0) cat("All saplings have a recognized Unit Group.<br>") else {
  cat( errortext("Saplings with a missing or unrecongized Unit Group:")); NiceTable(Saplings_Bad_Unit_Group)}

if(nrow(Saplings_Mismatch_Unit_Group)==0) cat("All saplings have Unit Group that is consistent with their Unit Code.<br>") else {
     cat(errortext("Saplings with a Unit Group that is inconsistent with their Unit Code:")); NiceTable(Saplings_Mismatch_Unit_Group)}

```

---

### Plot Names

```{r Sapling_plot_names, echo=FALSE, hold=FALSE, results="asis"}
if(nrow(Saplings_No_Plot_Name)==0) cat("All saplings have a Plot Name.<br>") else {
  errortext("Saplings with a missing Plot Name:"); NiceTable(Saplings_No_Plot_Name)}

```

---

### Event Panel, Frame and Cycle

```{r Sapling_Panel_Frame_Cycle,echo=FALSE, hold=FALSE, results="asis"}
 
cat("<br>**Sapling Panel Data**<br>")
if(nrow(Saplings_Bad_Panel)==0) cat("Each sapling has a panel code from 1 to 4.<br>") else {
errorText("Saplings without a panel code from 1-4:"); NiceTable(Saplings_Bad_Panel)}
  
cat("<br>**Sapling Frame Data**<br>")
if(nrow(Saplings_Bad_Frame)==0) cat("Each sapling has a frame that is either Region or Park.<br>") else {
errorText("Saplings without a frame of either Region or Park:"); NiceTable(Saplings_Bad_Frame)}
 
cat("<br>**Sapling Cycle Data**<br>")
if(nrow(Saplings_Bad_Cycle)==0) cat("Each saplings is from a cycle that matches its event year <br>") else {
errorText("Saplings without a cycle or with a cycle that does not match its event year:"); NiceTable(Saplings_Bad_Cycle)}

```

---

###  Dates
```{r Sapling_Dates, echo=FALSE, hold=FALSE, results="asis"}

if(nrow(Saplings_Bad_Date)==0) cat("All sapling dates match an event date.<br>") else {
  errorText("Saplings whose date does not match an event date:"); NiceTable(Sapling_Bad_Date)}
 
if(nrow(Saplings_Bad_Year)==0) cat("All sapling dates and sample years are consistent.<br>") else {
  errorText("Saplings whose date does not match its sample year:"); NiceTable(Saplings_Bad_Year)}

```

---

### Sapling Tag

```{r Sapling_Tag, echo=FALSE, hold=FALSE, results="asis"}

if(nrow(Saplings_Bad_Tag)==0) cat("All sapling records have a valid tag.<br>") else {
     errorText("Sapling records with no tag or a tag <1 or >30,000 tag:"); NiceTable(Saplings_Bad_Tag)}

if(nrow(Saplings_Duplicate_Tag)==0) cat("No tags are duplicated in a single visit.<br>") else {
   errorText("Saplings with duplicate tag records:"); NiceTable(Saplings_Duplicate_Tag)}

```

---

### Sapling Microplot

```{r Sapling_Microplot, echo=FALSE, hold=FALSE, results="asis"}
if(nrow(Saplings_Bad_Microplot)==0) cat("All saplings have a microplot of 60, 180 or 300.<br>") else {
    errorText("Saplings with a microplot number that is not 60, 180 or 300:"); NiceTable(Saplings_Bad_Microplot)}
```

---

### Species ID

```{r Sapling_Species, echo=FALSE, hold=FALSE, results="asis"}
 
if(nrow(Saplings_No_Name)==0) cat("All sapling records checked have a species ID.<br>") else {
  errorText("Saplings with no species name:"); NiceTable(Saplings_No_Name)}

if(nrow(Saplings_Many_Names)==0) cat("All saplings have only one species ID.<br>") else {
  errorText("Saplings with multiple species names:"); NiceTable(Saplings_Many_Names)}
 
if(nrow(Saplings_No_TSN)==0) cat("All sapling records checked have a TSN.<br>") else {
  errorText("Saplings with no TSN:"); NiceTable(Saplings_No_TSN)}
 
if(nrow(Saplings_Many_TSN)==0) cat("All saplings have only one TSN.<br>") else {
  errorText("Saplings with multiple TSB:"); NiceTable(Saplings_Many_TSN)}

```

---

### Sapling Stem Number

```{r Sapling_Stem_Number, echo=FALSE, hold=FALSE, results="asis"}

cat("<br>**Live Sapling Stem Number**<br>")
  if(nrow(Saplings_Live_Bad_Stems)==0) cat("All living sapling records have between one and five stems.<br>") else {
     errorText("Living sapling records with <1 or >5 stems:"); NiceTable(Saplings_Live_Bad_Stems)}

cat("<br>**Non-living  Sapling with Live Stems**<br>")
  if(nrow(Saplings_Unalive_Living_Stems)==0) cat("No non-living sapling records have live stems.<br>") else {
     errorText("Non-living sapling records with living stems not 0:"); NiceTable(Saplings_Unalive_Living_Stems)}

```

---

###  Sapling Status
```{r Sapling_Status, echo=FALSE, hold=FALSE, results="asis"}

if(nrow(Saplings_Bad_Status)==0) cat("All sapling records have a valid status.<br>") else {
   errorText("Sapling records without a status or a status we do not use:"); NiceTable(Saplings_Bad_Status)}

```

---


### Sapling Habit

```{r Sapling_Habit, echo=FALSE, hold=FALSE, results="asis"}

  if(nrow(Saplings_Bad_Habit)==0) cat("All sapling records have a habit of 'Tree'.<br>") else {
     errorText("Sapling records without a habit of 'Tree':"); NiceTable(Saplings_Bad_Habit)}

```

---


### Sapling Diameter

```{r Sapling_Diameter, echo=FALSE, hold=FALSE, results="asis"}
cat("<br>**DBH Check**<br>")
  if(nrow(Saplings_Bad_DBH_Check)==0) cat("No sapling records have an inappropriate DBH check.<br>") else { 
     errorText("Sapling records with the DBH check box checked before that was done or for tree with no DBH:<br>"); NiceTable(Saplings_Bad_DBH_Check)}
 
cat("<br>**Living Sapling DBH Incorrect**<br>")
  if(nrow(Saplings_Live_Bad_DBH)==0) cat("No living saplings records have an invlid DBH.<br>") else { 
     errorText("Live sapling records with a living DBH=0 or > 10cm:"); NiceTable(Saplings_Live_Bad_DBH)}

cat("<br>**Dead Saplings DBH Incorrect**<br>")   
 if(nrow(Saplings_Dead_Bad_DBH)==0) cat("No dead saplings have a mising or live DBH.<br>") else { 
     errorText("Dead sapling records with a living or missing DBH:"); NiceTable(Saplings_Dead_Bad_DBH)}
 
cat("<br>**DBH Wrongly Recorded**<br>")
 if(nrow(Saplings_Other_Bad_DBH)==0) cat("No saplings have a live DBH when they should not.<br>") else {
   errorText("Sapling records with a live DBH that should not have one:"); NiceTable(Saplings_Other_Bad_DBH)}

```

---


### Sapling Stem Diameter

```{r Sapling_Stem_Diameter, echo=FALSE, hold=FALSE, results="asis"}

cat("<br>**Living Stem DBH Incorrect**<br>")
  if(nrow(Sapling_Stems_Live_Bad_DBH)==0) cat("No live sapling stems have an invlid DBH.<br>") else { 
     errorText("Live sapling stem records with a missing DBH,  DBH <1 cm or DBH >0 10cm:"); NiceTable(Sapling_Stems_Live_Bad_DBH)}
  
cat("<br>**Dead Stem DBH Incorrect**<br>")
  if(nrow(Sapling_Stems_Dead_Bad_DBH)==0) cat("No dead sapling stems have an invlid DBH.<br>") else { 
     errorText("Dead sapling stem records with a missing DBH or a DBH <10 cm:"); NiceTable(Sapling_Stems_Dead_Bad_DBH)}
  
cat("<br>**Stem DBH Wrongly Recorded**<br>") 
  if(nrow(Sapling_Stems_Other_Bad_DBH)==0) cat("No sapling stems have a DBH when they should not.<br>") else { 
     errorText("Sapling stem records with a DBH on a tree that should not have any DBH:"); NiceTable(Sapling_Stems_Other_Bad_DBH)}

```

---

### Sapling Vigor

```{r Sapling_vigor, echo=FALSE, hold=FALSE, results="asis"}

cat("<br>** Disabled for 2020 data as this is not exported**<br>")

#  
# cat("<br>**Living Saplings Vigor Invalid**<br>") 
#   if(nrow(Saplings_Live_Bad_Vigor)==0) cat("All live saplings have a valid vigor.<br>") else {
#      errorText("Living sapling records with a vigor other than 0-5:"); NiceTable(Saplings_Live_Bad_Vigor)}
#   
# cat("<br>**Non-Living Saplings with Vigor**<br>")
#   if(nrow(Saplings_Unalive_Bad_Vigor)==0) cat("No non-living saplings have a vigor.<br>") else {
#      errorText("Non-living sapling records with a vigor:"); NiceTable(Saplings_Unalive_Bad_Vigor)}

```

---

### Saplings Foliage

Currently checked under Tree Foliage

```{r Sapling_Foliatge, echo=FALSE, hold=FALSE, results="asis"}
 
  # if(nrow(Trees_Bad_Foliage_Condition)==0) cat(paste(TotTrees, " Tree records checked and all foliage conditions are valid.  \n")) else {
  #    cat("Living tree records with invalid foliage conditions:  \n"); NiceTable(Trees_Bad_Foliage_Condition)}
  # 
  # if(nrow(Trees_Bad_Foliage_Condition)==0) cat(paste(TotTrees, " Tree records checked and all foliage percents are valid.  \n")) else {
  #    cat("Living tree records with invalid foliage percents:  \n"); NiceTable(Trees_Bad_Foliage_Percent)}
  # 
  # if(nrow(Trees_Unalive_Foliage)==0) cat(paste(TotTrees, " Tree records checked and no non-living trees have foliage condiditons.  \n")) else {
  #    cat("Non-living tree records with foliage conditions:  \n"); NiceTable(Trees_Unalive_Foliage)}
```

---

### Sapling Conditions

Currently checked under Tree Conditions

```{r Sapling_Conditions, echo=FALSE, hold=FALSE, results="asis"}
 
# if(nrow(Trees_Live_Bad_Tree_Condition)==0) cat(paste(TotTrees, " Tree records checked and all tree conditions are valid.  \n")) else {
#      cat("Living tree records with a tree condition we don't monitor:  \n"); NiceTable(Trees_Live_Bad_Tree_Condition)}
# 
# if(nrow(Trees_Live_Anachronistic_Tree_Conditions)==0) cat(paste(TotTrees, " Tree records checked and all tree conditions are from the correct year.  \n")) else {cat("Living tree records with a tree condition from the wrong year:  \n"); NiceTable(Trees_Live_Anachronistic_Tree_Conditions)}
# 
# if(nrow(Trees_Unalive_Tree_Conditions)==0) cat(paste(TotTrees, " Tree records checked and all non-living trees have no conditions.  \n")) else { cat("Non-living tree records with a tree condition:  \n"); NiceTable(Trees_Unalive_Tree_Conditions)}
# 
# 
# if(nrow(Trees_Bad_Vines)==0) cat(paste(TotTrees, " Tree records checked and with vines in the crown had vine records.  \n")) else { cat("Tree records with vines in the crown but no corresponding vine record:  \n"); NiceTable(Trees_Bad_Vines)}
```

---

### Sapling Pests

Currently checked under tree pests
```{r Sapling_Pests, echo=FALSE, hold=FALSE, results="asis"}
 
# if(nrow(Trees_Live_Bad_Pest)==0) cat(paste(TotTrees, " Tree records checked and all pest records are valid.  \n")) else {
#      cat("Living tree records with a pest we don't monitor:  \n"); NiceTable(Trees_Live_Bad_Pest)}
#  
#  if(nrow(Trees_Live_Anachronistic_Pest)==0) cat(paste(TotTrees, " Tree records checked and all pests are from the correct year.  \n")) else {cat("Living tree records with a pest from the wrong year:  \n"); NiceTable(Trees_Live_Anachronistic_Pest)}
#  
#  if(nrow(Trees_Unalive_Pest)==0) cat(paste(TotTrees, " Tree records checked and all non-living trees have no pests.  \n")) else {
#    cat("Non-living tree records with a pest:  \n"); NiceTable(Trees_Unalive_Pest)}
# 
#  
#  if(nrow(Trees_Pest_Bad_Host)==0) cat(paste(TotTrees, " Tree records checked and no pests on incorrect host species.  \n")) else {
#    cat("Trees with inconsistent host species - pest pairs:  \n"); NiceTable(Trees_Pest_Bad_Host)}

```

---

### Sapling Browse

```{r Sapling_Browse, echo=FALSE, hold=FALSE, results="asis"}
 
cat("<br>**Living Saplings Browsable Status Invalid**<br>") 
  if(nrow(Saplings_Live_Bad_Browsable)==0) cat("All live saplings have a valid browsable status.<br>") else {
     errorText("Living sapling records with a browsable status other than Yes, No, or unk:"); NiceTable(Saplings_Live_Bad_Browsable)}
  

cat("<br>**Living Saplings Anachronistic Browsable Status**<br>") 
  if(nrow(Saplings_Live_Anachronistic_Browsable)==0) cat("No living saplings records have a browsable status before 2010.<br>") else {
     errorText("Living sapling records with a browsable status before 2010:"); NiceTable(Saplings_Live_Anachronistic_Browsable)}
  

 cat("<br>**Non-Living Saplings with Browsable Status**<br>")
   if(nrow(Saplings_Unalive_Browsable)==0) cat("No non-living saplings have a browsable status.<br>") else {
      errorText("Non-living sapling records with a browsable status:"); NiceTable(Saplings_Unalive_Browsable)}

 cat("<br>**Living Saplings Browsed Status Invalid**<br>") 
  if(nrow(Saplings_Live_Bad_Browsed)==0) cat("All live saplings have a valid browsed status.<br>") else {
     errorText("Living sapling records with a browsed status other than Yes, or No:"); NiceTable(Saplings_Live_Bad_Browsed)}
   
 cat("<br>**Non-Living Saplings with Browsed Status**<br>")
   if(nrow(Saplings_Unalive_Browsed)==0) cat("No non-living saplings have a browsed status.<br>") else {
      errorText("Non-living sapling records with a browsed status:"); NiceTable(Saplings_Unalive_Browsed)}
 
  cat("<br>**Living Saplings with Illogical Browsing**<br>")
   if(nrow(Saplings_Live_Illogical_Browse)==0) cat("No living saplings have contradictory browsable and browsed status.<br>") else {
      errorText("Living sapling records with a browsable status of 'No' and browsed status of 'Yes':"); NiceTable(Saplings_Live_Illogical_Browse)}
 
```

---

### **Change Over Time**

### Sapling Status Discrepancies

```{r Sapling_Status_Change, echo=FALSE, hold=FALSE, results="asis"}
 
 cat("<br>**Saplings that Start in a Non-Sampled Status**<br>")
  if(nrow(Saplings_Start_Wrong)==0) cat("No saplings start as missing downgraded, or dead fallen.<br>") else {
    errorText("Saplings that start in a non-sampled status:"); NiceTable(Saplings_Start_Wrong)}
 
 cat("<br>**Saplings that are Sampled after they are Dead**<br>")
  if(nrow(Saplings_Dead_Plus)==0) cat("No sapling was sampled after it was dead.<br>") else {
    errorText("Saplings that were reorded as dead and then sampled again:"); NiceTable(Saplings_Dead_Plus)}

 
 cat("<br>**Saplings that Fell Down and then Levitated Back Up**<br>")
  if(nrow(Saplings_Levitated)==0) cat("No sapling was Alive Fallen and then became Standing or Leaning.<br>") else {
    errorText("Saplings that were Alive Fallen but then became Standing or Leaning:"); NiceTable(Saplings_Levitated)}
 
 cat("<br>**Saplings that went Missing and were Found Alive**<br>")
  if(nrow(Saplings_Found_Alive)==0) cat("No sapling was Missing and then found Alive.<br>") else {
    errorText("Saplings that were Missing but then were found Alive:"); NiceTable(Saplings_Found_Alive)}
 
 cat("<br>**Saplings that were Downgraded and resampled**<br>")
  if(nrow(Saplings_Downgraded_Persisting)==0) cat("No sapling was resampled after being downgraded.<br>") else {
    errorText("Saplings that were Downgraded but then were resampled:"); NiceTable(Saplings_Downgraded_Persisting)}

 cat("<br>**Saplings that went Missing Three Times in a Row**<br>")
  if(nrow(Saplings_Triple_Missing)==0) cat("No sapling went missing 3 consecutive visits.<br>") else {
    errorText("Saplings that were Missing three times in a row:"); NiceTable(Saplings_Triple_Missing)}

```

---

### Sapling Vigor Change
```{r Sapling_Vigor_Change, echo=FALSE, hold=FALSE, results="asis"}

 cat("<br>**Saplings that have a Large Improvement in Vigor**<br>")
  if(nrow(Saplings_Vigor_Jump)==0) cat("No sapling has a 2 class improvement in vigor.<br>") else {
    errorText("Saplings that have a 2 class improvement in vigor:"); NiceTable(Saplings_Vigor_Jump)}
```


---

### Sapling DBH Change
```{r Sapling_Live_DBH_Change, echo=FALSE, hold=FALSE, results="asis"}

 cat("<br>**Saplings that have a large change in Live DBH**<br>")
  if(nrow(Saplings_Live_Large_DBH_change)==0) cat("No sapling has had a 3cm change in live DBH.<br>") else {
    errorText("Saplings that have had a 3cm change in live DBH:"); NiceTable(Saplings_Live_Large_DBH_change)}
 
 cat("<br>**Saplings that have a large starting DBH**<br>")
  if(nrow(Saplings_Start_Too_Large)==0) cat("No saplings starts with a >3cm DBH after a plot is established.<br>") else {
    errorText("Saplings that start with a >3cm DBH after a plot is established:"); NiceTable(Saplings_Start_Too_Large)}

```

---

### Sapling Condition Change

Currently checked under Tree Condition Change
```{r Sapoling_Condition_Change, echo=FALSE, hold=FALSE, results="asis"}

# cat("<br>**Trees that had EAB and then later did not**<br>")
#  if(nrow(Trees_Lose_EAB)==0) cat("No tree had EAB and then lost it.<br>") else {
#    errorText("Trees that had EAB and then lost it:"); NiceTable(Trees_Lose_EAB)}
# 
# cat("<br>**Trees that had Dogwood Anthracnose and then later did not**<br>")
#  if(nrow(Trees_Lose_Anthracnose)==0) cat("No tree had Dogwood Anthracnose and then lost it.<br>") else {
#    errorText("Trees that had Dogwood Anthracnose and then lost it:"); NiceTable(Trees_Lose_Anthracnose)}
# 
# cat("<br>**Trees that had Hemlock Scale and then later did not**<br>")
#  if(nrow(Trees_Lose_Scale)==0) cat("No tree had Hemlock Scale and then lost it.<br>") else {
#    errorText("Trees that had Hemlock Scale and then lost it:"); NiceTable(Trees_Lose_Scale)}
# 
# cat("<br>**Trees that had Hemlock Wooly Adelgid and then later did not**<br>")
#  if(nrow(Trees_Lose_Adelgid)==0) cat("No tree had Hemlock Wooly Adelgid and then lost it.<br>") else {
#    errorText("Trees that had Hemlock Wooly Adelgid and then lost it:"); NiceTable(Trees_Lose_Adelgid)}
# 
# cat("<br>**Trees that had exposed roots and then later did not**<br>")
#  if(nrow(Trees_Lose_ExpRoots)==0) cat("No tree had exposed roots and then lost it.<br>") else {
#    errorText("Trees that had exposed roots and then lost it:"); NiceTable(Trees_Lose_ExpRoots)}
# 
# cat("<br>**Trees that were hollow and then later were not**<br>")
#  if(nrow(Trees_Lose_Hollow)==0) cat("No tree was hollow and then lost it.<br>") else {
#    errorText("Trees that were hollow and then lost it:"); NiceTable(Trees_Lose_Hollow)}
# 
# cat("<br>**Trees that had vines in the crown and then later did not**<br>")
#  if(nrow(Trees_Lose_Vine_Crown)==0) cat("No tree had vines in the crown and then lost it.<br>") else {
#    errorText("Trees that had vines in the crown and then lost it:"); NiceTable(Trees_Lose_Vine_Crown)}
# 
# cat("<br>**Trees that had vine stress and then later did not**<br>")
#  if(nrow(Trees_Lose_Vine_Stress)==0) cat("No tree had vine stress and then lost it.<br>") else {
#    errorText("Trees that had vine stress and then lost it:"); NiceTable(Trees_Lose_Vine_Stress)}
# 
# cat("<br>**Trees that had changed number of conditions**<br>")
#  if(nrow(Trees_Change_Conditon_Number)==0) cat("No trees changed number of conditions.<br>") else {
#    errorText("Trees that changed number of conditiosn:"); NiceTable(Trees_Change_Conditon_Number)}
```




