---
title: "Forest Vegetation Tree QC"
author: "John Paul Schmit"
date: "5/19/2020"
output: html_document
---


```{r tree_setup, include=F}
TotTrees<-nrow(QCTrees) #Total Number of tree records checked
TotStems<-nrow(QCStems) #Total number of stem records checked


Trees_Bad_Status<-QCTrees %>% filter(is.na(Status) | !Status %in% c(Live_Status, Dead_Status, Missing_Status, Other_Status) ) %>%
  select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status)

Trees_No_Name<-QCTrees %>% filter(Latin_Name=="") %>%
  select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name)

Trees_Bad_Tag<-QCTrees %>% filter(is.na(Tag) | Tag < 1 | Tag>30000) %>%
  select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name)

## Crown class

Trees_Live_Bad_Crown<-QCTrees %>% filter(Status %in% Live_Status & (Crown_Description=="" | !Crown_Description %in% 
   c("Co-dominant", "Dominant", "Edge Tree", "Intermediate", "Light Gap Exploiter", "Open-grown", "Overtopped" ))) %>%
  select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Crown_Description)

Trees_Unalive_Bad_Crown<-QCTrees %>% filter(!Status %in% Live_Status & Crown_Description!="") %>%
  select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Crown_Description)

Trees_Bad_DBH_Check <-QCTrees %>% filter( (Sample_Year<2018 & DBH_Check) | 
      (Sample_Year>2017 & DBH_Check & 
          Status %in% c(Missing_Status, "Dead Fallen", "Dead Missing", "Dead - Too Small", Other_Status))) %>% 
    select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, DBH_Check)

## DBH

Trees_Live_Bad_DBH<-QCTrees %>% filter(Status %in% Live_Status & (
   (is.na(Equiv_Live_DBH_cm) | Equiv_Live_DBH_cm < 10 | is.na(Equiv_Dead_DBH_cm) | ( Equiv_Dead_DBH_cm>0 & Equiv_Dead_DBH_cm < 10)) ))  %>% 
   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Equiv_Live_DBH_cm, Equiv_Dead_DBH_cm)

Trees_Dead_Bad_DBH<-QCTrees %>% filter(Status %in% c("Dead Leaning", "Dead Standing") & (
   (is.na(Equiv_Dead_DBH_cm) | Equiv_Dead_DBH_cm < 10 | is.na(Equiv_Live_DBH_cm) | Equiv_Live_DBH_cm>=10 |
      ( Equiv_Live_DBH_cm >0 & Equiv_Live_DBH_cm < 1)) ))  %>% 
   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Equiv_Live_DBH_cm, Equiv_Dead_DBH_cm)

Trees_Other_Bad_DBH<-QCTrees %>% filter(Status %in% c(Missing_Status, Other_Status, 
    "Dead", "Dead - Human Action", "Dead - Too Small", "Dead Fallen", "Dead Missing") & (
   (is.na(Equiv_Dead_DBH_cm) |is.na(Equiv_Live_DBH_cm) | Equiv_Live_DBH_cm!=0 |
       Equiv_Dead_DBH_cm !=0 )) )  %>% 
   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Equiv_Live_DBH_cm, Equiv_Dead_DBH_cm)

Tree_Stems_Live_Bad_DBH<-QCStems %>% filter(Sample_Year %in% QCYears, Live==T & Class=="Tree", (is.na(DBH) | DBH<1)) %>% 
  select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, DBH, Live )

Tree_Stems_Dead_Bad_DBH<-QCStems %>% filter(Sample_Year %in% QCYears, Live==F & Class=="Tree", (is.na(DBH) | DBH<10)) %>% 
  select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, DBH, Live )

Tree_Stems_Other_Bad_DBH<-QCStems %>% filter(Sample_Year %in% QCYears, Status %in% c(Missing_Status, Other_Status, 
    "Dead", "Dead - Human Action", "Dead - Too Small", "Dead Fallen", "Dead Missing")) %>% 
  select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, DBH, Live )

Trees_Live_Bad_Vigor<-QCTrees %>% filter(Status %in% Live_Status & 
      ( (Sample_Year<2017 & !is.na(TreeVigor)) | (Sample_Year >=2017 & (is.na(TreeVigor)  | !TreeVigor %in% 0:5)) )) %>% 
   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, TreeVigor, VigorClass)

## Vigor
Trees_Unalive_Bad_Vigor<-QCTrees %>% filter(!Status %in% Live_Status & !is.na(TreeVigor)) %>% 
   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, TreeVigor, VigorClass)

## Foliage
Trees_Bad_Foliage_Condition<-QCFoliage %>% filter(Sample_Year  %in% QCYears & (is.na(Condition_Description) | 
              !Condition_Description %in% c("Chlorosis","Holes","Necrosis","Small leaves","Wilting","Other") )) %>% 
  select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Condition_Description, Percent_Afflicted)
  

Trees_Bad_Foliage_Percent<-QCFoliage %>% filter(Sample_Year  %in% QCYears & (is.na(Percent_Afflicted) | 
                            Percent_Afflicted<1 |Percent_Afflicted>100)) %>% 
    select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Condition_Description, Percent_Afflicted)

Trees_Unalive_Foliage<- QCFoliage %>% filter(Sample_Year %in% QCYears & !Status %in% Live_Status ) %>% 
    select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Status, Condition_Description, Percent_Afflicted)


## Tree Conditions
Trees_Live_Bad_Tree_Condition<-QCConditions %>% filter(Sample_Year %in% QCYears & !Pest & Status %in% Live_Status &
  !Condition %in% c("Advanced decay", "Primary branch broken",  "Large dead branches", "Lightning Damage", "Wind Damage", "Buck Rub", "Bark Damage",
                    "Beaver Damage", "Human Damage", "Mammal Damage", "Bird Damage", "Exposed roots", "Epicormic sprouts", "Fungus", "Fire", "Hollow",
                    "Sparse foliage", "Open wound", "Vines in the crown",  "Vine stress", "Other visible condition", "Other visible damage")) %>% 
  select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Condition)

Trees_Live_Anachronistic_Tree_Conditions<-QCConditions %>% filter(Sample_Year %in% QCYears & !Pest & Status %in% Live_Status &
      (
        (Condition =="Lightning Damage" & Sample_Year< 2009) | 
          (Condition %in% c("Buck Rub", "Bark Damage", "Human Damage") & Sample_Year < 2014) |
          (Condition =="Beaver Damage" & !Sample_Year %in% 2014:2016) |
          (Condition =="Epicormic Sprouts" & Sample_Year< 2015) |
          (Condition %in% c("Mammal Damage", "Bird Damage", "Exposed roots", "Fungus", "Fire", "Hollow", "Sparse foliage",
                            "Other visible condition") & Sample_Year < 2017) |
          (Condition =="Vine Stress" & Sample_Year< 2015) |
         (Condition =="Other visible damage" & Sample_Year> 2016)
        )) %>%   select(Unit_Code, Plot_Name, Sample_Year, Tag, Latin_Name, Condition)



```

- should not start as missing, earlier ones should not start as dead, never start as dead fallen

- dead trees wth > 1cm live dbh should not exist in a microplot as it would be a sapling


- tree conditions only on live trees, except for EAB on dead. never on missing. should be from list that was current.
- if condition is vines in crown, should have 1 or more vines on it. 
- should have a distance and azimuth <15m and between 0 and 360 (but not 0)
- How do we deal with removed from study? Need to check that everything that was suppsoed to be monitored was actualy monitored
- Tree disease on correct species



###  Tree Status
```{r Tree_Status, echo=FALSE, hold=FALSE, results="asis"}

if(nrow(Trees_Bad_Status)==0) cat(paste(TotTrees, " Tree records checked and all have a valid status.  \n")) else {
   cat("Tree records with a missing status or a status we do not use:  \n"); NiceTable(Trees_Bad_Status)}

```

---

### Species ID

```{r Tree_Species, echo=FALSE, hold=FALSE, results="asis"}
 
 if(nrow(Trees_No_Name)==0) cat(paste(TotTrees, " Tree records checked and all have a species ID.  \n")) else {
    cat("Tree records with no species name:  \n"); NiceTable(Trees_No_Name)}

```


---

### Tree Tag

```{r Tree_Tag, echo=FALSE, hold=FALSE, results="asis"}
 if(nrow(Trees_Bad_Tag)==0) cat(paste(TotTrees, " Tree records checked and all have a valid tag.  \n")) else {
    cat("Tree records with no tag or a tag <1 or >30,000 tag:  \n"); NiceTable(Trees_Bad_Tag)}

```

---

### Tree Crown

```{r Tree_Crown, echo=FALSE, hold=FALSE, results="asis"}
 
 if(nrow(Trees_Live_Bad_Crown)==0) cat(paste(TotTrees, " Tree records checed and all living trees have a valid crown description.  \n")) else {
    cat("Living Tree records with a mising crown description or one we do not use:  \n"); NiceTable(Trees_Live_Bad_Crown)}

 if(nrow(Trees_Unalive_Bad_Crown)==0) cat(paste(TotTrees, " Tree records checked and no non-living trees have a crown description.  \n")) else { 
    cat("Non-living tree records with a crown description:  \n"); NiceTable(Trees_Unalive_Bad_Crown)}
```

---

### Tree Diameter

```{r Tree_Diameter, echo=FALSE, hold=FALSE, results="asis"}

 if(nrow(Trees_Bad_DBH_Check)==0) cat(paste(TotTrees, " Tree records checked and none have an inappropriate DBH check.  \n")) else { 
    cat("Tree records with the DBH check box checked before that was done or for tree with no DBH:  \n"); NiceTable(Trees_Bad_DBH_Check)}

 if(nrow(Trees_Live_Bad_DBH)==0) cat(paste(TotTrees, " Tree records checked and no live trees have an invlid DBH.  \n")) else { 
    cat("Live tree records with a livign or dead DBH < 10cm:  \n"); NiceTable(Trees_Live_Bad_DBH)}
 
if(nrow(Trees_Dead_Bad_DBH)==0) cat(paste(TotTrees, " Tree records checked and no dead trees have an invlid DBH.  \n")) else { 
    cat("Dead tree records with a living or dead DBH <10cm:  \n"); NiceTable(Trees_Dead_Bad_DBH)}

if(nrow(Trees_Other_Bad_DBH)==0) cat(paste(TotTrees, " Tree records checked and no trees have a DBH when they should not.  \n")) else { 
    cat("Tree records with a DBH that should not have one:  \n"); NiceTable(Trees_Other_Bad_DBH)}

```

---


### Stem Diameter

```{r Stem_Diameter, echo=FALSE, hold=FALSE, results="asis"}

 if(nrow(Tree_Stems_Live_Bad_DBH)==0) cat(paste(TotStems, " Stems records checked and no live stems have an invlid DBH.  \n")) else { 
    cat("Live stem records with a missing DBH or a DBH <1 cm:  \n"); NiceTable(Tree_Stems_Live_Bad_DBH)}

 if(nrow(Tree_Stems_Dead_Bad_DBH)==0) cat(paste(TotStems, " Stems records checked and no dead stems have an invlid DBH.  \n")) else { 
    cat("Dead stem records with a missing DBH or a DBH <10 cm:  \n"); NiceTable(Tree_Stems_Dead_Bad_DBH)}
 
 if(nrow(Tree_Stems_Other_Bad_DBH)==0) cat(paste(TotTrees, " Stem records checked and no stems have a DBH when they should not.  \n")) else { 
    cat("Stem records with a DBH on a tree that should not have any DBH:  \n"); NiceTable(Tree_Stems_Other_Bad_DBH)}

```

---



### Tree Vigor

```{r Tree_vigor, echo=FALSE, hold=FALSE, results="asis"}
 
 if(nrow(Trees_Live_Bad_Vigor)==0) cat(paste(TotTrees, " Tree records checked and all live trees have a valid vigor.  \n")) else {
    cat("Living tree records with a vigor other than 0-5:  \n"); NiceTable(Trees_Live_Bad_Vigor)}

 if(nrow(Trees_Unalive_Bad_Vigor)==0) cat(paste(TotTrees, " Tree records checked and no non-living trees have a vigor.  \n")) else {
    cat("Non-living tree records with a vigor:  \n"); NiceTable(Trees_Unalive_Bad_Vigor)}

```

### Tree Foliage

```{r Tree_Foliatge, echo=FALSE, hold=FALSE, results="asis"}
 
  if(nrow(Trees_Bad_Foliage_Condition)==0) cat(paste(TotTrees, " Tree records checked and all foliage conditions are valid.  \n")) else {
     cat("Living tree records with invalid foliage conditions:  \n"); NiceTable(Trees_Bad_Foliage_Condition)}
  
  if(nrow(Trees_Bad_Foliage_Condition)==0) cat(paste(TotTrees, " Tree records checked and all foliage percents are valid.  \n")) else {
     cat("Living tree records with invalid foliage percents:  \n"); NiceTable(Trees_Bad_Foliage_Percent)}
  
  if(nrow(Trees_Unalive_Foliage)==0) cat(paste(TotTrees, " Tree records checked and no non-living trees have foliage condiditons.  \n")) else {
     cat("Non-living tree records with foliage conditions:  \n"); NiceTable(Trees_Unalive_Foliage)}
```


### Tree Conditions

```{r Tree_Condition, echo=FALSE, hold=FALSE, results="asis"}
 
if(nrow(Trees_Live_Bad_Tree_Condition)==0) cat(paste(TotTrees, " Tree records checked and all tree conditions are valid.  \n")) else {
     cat("Living tree records with a tree condition we don't monitor:  \n"); NiceTable(Trees_Live_Bad_Tree_Condition)}
if(nrow(Trees_Live_Anachronistic_Tree_Conditions)==0) cat(paste(TotTrees, " Tree records checked and all tree conditions are from the correct year.  \n")) else {cat("Living tree records with a tree condition from the wrong year:  \n"); NiceTable(Trees_Live_Anachronistic_Tree_Conditions)}


```

